---
title: "Generalizability Analysis Script"
author: "Zachary Houghton"
date: "2023-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(brms)
library(sjPlot)
```

## Conditions Table

Table1:

|                |            |           |                |            |           |                  |            |           |
|--------|--------|--------|--------|--------|--------|--------|--------|--------|
| **Condition1** | #of tokens | #of types | **Condition2** | #of tokens | #of types | **Condition3**   | #of tokens | #of types |
| dan            | 12         | 12        | dan            | 12         | 3         | dan              | 12         | 12        |
| nem            | 12         | 3         | nem            | 3          | 3         | nem              | 3          | 3         |
| sil            | 6          | 6         | sil            | 6          | 6         | sil              | 6          | 6         |
| shoon          | 6          | 6         | shoon          | 6          | 6         | shoon            | 6          | 6         |
| **Condition4** |            |           | **Condition5** |            |           | **nem language** | #of tokens | #of types |
| dan            | 12         | 3         | dan            | 3          | 3         | dan              | 3          | 3         |
| nem            | 12         | 12        | nem            | 12         | 3         | nem              | 12         | 12        |
| sil            | 6          | 6         | sil            | 6          | 6         | sil              | 6          | 6         |
| shoon          | 6          | 6         | shoon          | 6          | 6         | shoon            | 6          | 6         |

Table2

|               |               |               |               |                 |              |              |              |                |
|--------|:------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|
| **Condition** | **dan token** | **nem token** | **sil token** | **shoon token** | **dan type** | **nem type** | **sil type** | **shoon type** |
| 1             |      12       |      12       |       6       |        6        |      12      |      3       |      6       |       6        |
| 2             |      12       |       3       |       6       |        6        |      3       |      3       |      6       |       6        |
| 3             |      12       |       3       |       6       |        6        |      12      |      3       |      6       |       6        |
| 4             |      12       |      12       |       6       |        6        |      3       |      12      |      6       |       6        |
| 5             |       3       |      12       |       6       |        6        |      3       |      3       |      6       |       6        |
| 6             |       3       |      12       |       6       |        6        |      3       |      12      |      6       |       6        |

|                 | Frequent Token | Frequent Type | Infrequent Token | Infrequent Type | Frequent Competitor Token | Frequent Competitor Type | Infrequent Competitor Token | Infrequent Competitor Type |
|--------|--------|--------|--------|--------|--------|--------|--------|--------|
| **Condition 1** | 12             | 12            | 12               | 3               | 6                         | 6                        | 6                           | 6                          |
| **Condition 2** | 12             | 3             | 3                | 3               | 6                         | 6                        | 6                           | 6                          |
| **Condition 3** | 12             | 12            | 3                | 3               | 6                         | 6                        | 6                           | 6                          |

|                 | Frequent Token | Frequent Type | Infrequent Token | Infrequent Type |
|---------------|---------------|---------------|---------------|---------------|
| **Condition 1** | 12             | 12            | 12               | 3               |
| **Condition 2** | 12             | 3             | 3                | 3               |
| **Condition 3** | 12             | 12            | 3                | 3               |

## Data Preparation

First let's load our data and clean it up

<!--# confirm the number of items in the table (*5) matches the items given to participants -->

```{r message = F}
data = read_csv('../Data/raw_data.csv') %>%
  filter(is.na(PROLIFIC_PID) == F)

training_received = data %>%
  select(stem, suffix, label, condition, participant) %>%
  group_by(participant, condition, suffix) %>%
  summarize(table(suffix))


data_analysis = data %>%
  dplyr::select(participant, date, condition, pretraining, textbox.text, textbox_5.text, textbox_6.text, prod_label, prod_condition, prod_image2, prod_resp.text, key_resp_16.keys, comp_label1_location, comp_label2_location, label1, label2, comp_condition_stem, comp_condition_suffix, stem) %>%
  rename(age = textbox.text,
         native_lang = textbox_5.text,
         other_langs = textbox_6.text,
         fc_resp = key_resp_16.keys,
         fc_label1_location = comp_label1_location,
         fc_label2_location = comp_label2_location,
         fc_label1 = label1,
         fc_label2 = label2,
         prod_suffix = prod_image2,
         fc_condition_stem = comp_condition_stem,
         fc_condition_suffix = comp_condition_suffix,
         prod_resp = prod_resp.text,
         prod_stem = prod_label,
         resp_stem = stem) %>%
  group_by(participant) %>%
  fill(c(condition, pretraining, age, native_lang, other_langs)) 

data_analysis$date = gsub('_.*', '', data_analysis$date)
data_analysis$date = as.Date(data_analysis$date)

#data_analysis = data_analysis %>%
  #filter(date > '2023-10-11')

data_analysis$pretraining = as.factor(data_analysis$pretraining / 100)
data_analysis$condition = as.factor(data_analysis$condition)
data_analysis = data_analysis %>%
  mutate(fc_condition_suffix = ifelse(fc_condition_suffix == 'big', 'big_pl', fc_condition_suffix))

data_analysis_2afc = data_analysis %>%
  select(participant, date, condition, pretraining, age, native_lang, other_langs, fc_resp, fc_label1_location, fc_label2_location, fc_label1, fc_label2, fc_condition_stem, fc_condition_suffix, resp_stem) %>%
  drop_na(fc_resp)



data_analysis_prod = data_analysis %>%
  select(participant, condition, pretraining, age, native_lang, other_langs, prod_stem, prod_suffix, prod_condition, prod_resp) %>%
  drop_na(prod_resp)

data_analysis_prod$prod_suffix = gsub('.*/[0-9]*_(.+)\\.PNG', '\\1', data_analysis_prod$prod_suffix)

data_analysis_prod$prod_suffix[data_analysis_prod$prod_suffix=='2'] = 'big_pl'






```

There are quite a lot of typos, so now we'll manually go through the production data and correct the typos:

```{r}

data_analysis_prod_typos = data_analysis_prod %>%
  filter(prod_suffix == 'dim_pl')
write_csv(data_analysis_prod_typos, '../Data/prod_data_typos.csv')
```

The new

```{r}
#bad participants are participants who answered with only the stem (no suffix) more than 3 times out of the 6 production trials

bad_participants = c(587224, 290293, 145728, 506635, 184163, 380540, 273582, 393594, 224199, 852588, 710021, 545966, 378417, 816402, 218288, 547169, 265999, 665400, 074739, 566041, 613576, 502111, 020421, 549581, 558055, 824602, 876744, 030454, 528285, 358728, 058790, 528277, 220692, 053974, 465695, 768014, 721546, 939022, 098320, 933341, 381378, 120181, 077376, 060995, 330080, 028266, 982680, 120064, 822991, 252853, 375398, 349886, 978708, 259663, 493215, 945830, 477678, 239146, 042113, 617377, 595236, 828730, 000377, 781565


#bad_participants as of 2/14/24

)

length(bad_participants) #oh boy, 64 is a lot...
data_analysis_prod = read_csv('../Data/data_analysis_prod_typos_fixed.csv') %>%
  filter(!participant %in% bad_participants)

# data_analysis_prod = data_analysis_prod %>%
#   mutate(prod_resp_suffix = str_extract_all(prod_resp_fixed, 'dan|sil|shoon|nem')) %>%
#   unnest(prod_resp_suffix, keep_empty = T)
 data_analysis_prod = data_analysis_prod %>%
   mutate(prod_resp_suffix = prod_resp_fixed)
 
data_analysis_2afc = data_analysis_2afc %>%
  mutate(resp = ifelse(fc_resp == fc_label1_location, fc_label1, fc_label2))

data_analysis_2afc = data_analysis_2afc %>%
  mutate(resp_suffix = str_extract_all(resp, 'dan|sil|shoon|nem')) %>%
  unnest(resp_suffix, keep_empty = T)

data_analysis_2afc = data_analysis_2afc %>%
  mutate(accuracy = case_when(fc_condition_suffix == 'big_pl' ~ ifelse(resp_suffix %in% c('dan', 'sil'), 1, 0))) %>%
  mutate(accuracy = case_when(fc_condition_suffix == 'dim_sg' ~ ifelse(resp_suffix %in% c('nem', 'shoon'), 1, 0)))

# accuracy_scores = data_analysis_2afc %>% f
#   group_by(participant) %>%
#   filter(!is.na(accuracy)) %>%
#   summarize(mean(accuracy))

data_analysis_2afc = data_analysis_2afc %>%
  mutate(freq_choice = ifelse(condition %in% c(1,2,3), 
                              ifelse(resp_suffix == 'dan', 'freq',
                              ifelse(resp_suffix == 'sil', 'freq_competitor',
                              ifelse(resp_suffix == 'nem', 'infreq', 'infreq_competitor'))),
         ifelse(resp_suffix == 'nem', 'freq', #if condition is 4,5, or 6
         ifelse(resp_suffix == 'dan', 'infreq',
         ifelse(resp_suffix == 'shoon', 'freq_competitor', 'infreq_competitor')))))


data_analysis_prod = data_analysis_prod %>%
  mutate(freq_choice = ifelse(condition %in% c(1,2,3), 
                              ifelse(prod_resp_suffix == 'dan', 'freq',
                              ifelse(prod_resp_suffix == 'sil', 'freq_competitor',
                              ifelse(prod_resp_suffix == 'nem', 'infreq', 'infreq_competitor'))),
         ifelse(prod_resp_suffix == 'nem', 'freq', #if condition is 4,5, or 6
         ifelse(prod_resp_suffix == 'dan', 'infreq',
         ifelse(prod_resp_suffix == 'shoon', 'freq_competitor', 'infreq_competitor')))))


names = c('resp_stem', 'picture_meaning', 'stem_condition', 'resp', 'resp_suffix_form')
names_2afc = c('stem_condition', 'picture_meaning', 'resp_stem', 'resp', 'resp_suffix_form')

colnames(data_analysis_prod)[8:12] = names
colnames(data_analysis_2afc)[13:17] = names_2afc


data_analysis_prod = data_analysis_prod %>%
  mutate(accuracy = case_when(picture_meaning == 'big_pl' ~ ifelse(resp_suffix_form %in% c('dan', 'sil'), 1, 0))) %>%
  mutate(accuracy = case_when(picture_meaning == 'dim_sg' ~ ifelse(resp_suffix_form %in% c('nem', 'shoon'), 1, 0)))

data_analysis_2afc = data_analysis_2afc %>%
  select(participant, condition, pretraining, age, native_lang, other_langs, stem_condition, picture_meaning, resp_stem, resp, resp_suffix_form, freq_choice, accuracy) %>%
  mutate(task = '2afc')

data_analysis_prod = data_analysis_prod %>%
  mutate(task = 'prod')

#data_analysis_prod$date = as.Date(data_analysis_prod$date)
data_analysis_prod$condition = factor(data_analysis_prod$condition)
data_analysis_prod$pretraining = factor(data_analysis_prod$pretraining)

# data_analysis_2afc$date = as.character(data_analysis_2afc$date)
# data_analysis_2afc$condition = as.numeric(as.character(data_analysis_2afc$condition))
# data_analysis_2afc$pretraining = as.numeric(as.character(data_analysis_2afc$pretraining))

data_analysis = data_analysis_2afc %>%
  full_join(data_analysis_prod) 


accuracy_scores = data_analysis %>%
  filter(!is.na(accuracy) & task == '2afc') %>%
  group_by(participant) %>%
  summarize(mean_accuracy = mean(accuracy), sd_accuracy = sd(accuracy))
```

```{r}
data_analysis = data_analysis %>%
  mutate(meaning_choice = ifelse(condition %in% c(1,2,3), 
                              ifelse(picture_meaning == 'big_pl', 'freq',
                              ifelse(picture_meaning == 'dim_sg', 'infreq', 'novel')),
         ifelse(picture_meaning == 'big_pl', 'infreq', #if condition is 4,5, or 6
         ifelse(picture_meaning == 'dim_sg', 'freq', 'novel'))))

data_analysis = data_analysis %>%
  mutate(condition = ifelse(condition == 4, 1, 
                            ifelse(condition == 5, 2, 
                                   ifelse(condition == 6, 3, condition)))) %>%
  filter(!is.na(resp_suffix_form)) %>%
  left_join(accuracy_scores, by = 'participant')

```

# Analysis

First we'll eliminate participants with below \_\_\_% accuracy

```{r}
# accuracy_threshold = 0.7
# data_analysis_m1 = data_analysis %>%
#   filter(!mean_accuracy < accuracy_threshold)
```

Our dependent measure will be `freq_choice`.

Our independent measures will be pretraining, condition, stem_condition (whether the stem was familiar or novel), and task

<!--# add predictions? -->

<!--# analyses: freq_choice ~ pretraining*condition*stem_condition*task + (1|stem) + (1 + stem_condition*task|participant) + (pretraining*condition*task|stem) -->

<!--# freq vs infreq for novel meanings -->

<!--# freq vs freq competitor for novel meanings -->

<!--# also add analyses for subset data, subsetting by stem_condition and picture_meaning -->

```{r}
options (contrasts = c('contr.treatment','contr.treatment'))
#options(contrasts = c("contr.sum","contr.sum"))
data_m1 = data_analysis %>%
  filter(picture_meaning == 'dim_pl') %>%
  filter(freq_choice %in% c('freq', 'infreq')) %>% #we are discarding sil and shoon responses by doing this
  mutate(freq_choice = ifelse(freq_choice == 'freq', 1, 0)) %>%
  mutate(condition = as.factor(condition)) %>%
  mutate(participant = as.factor(participant)) %>%
  mutate(pretraining = as.factor(pretraining)) 
 
data_m1$condition = factor(data_m1$condition, levels = c(3, 1, 2)) 

data_familiar = data_m1 %>%
  filter(stem_condition == 'familiar')

data_novel = data_m1 %>%
  filter(stem_condition == 'novel')


#length(unique(data_m1$participant))
#length(unique(data_familiar$participant))


# priors_m1 = c(
#   prior(student_t(3, 0, 2), class = 'Intercept', dpar = 'mufreqcompetitor'),
#   prior(student_t(3, 0, 2), class = 'sd', dpar = 'mufreqcompetitor'),
#   prior(student_t(3, 0, 2), class = 'b', dpar = 'mufreqcompetitor'),
#   prior(student_t(3, 0, 2), class = 'Intercept', dpar = 'muinfreqcompetitor'),
#   prior(student_t(3, 0, 2), class = 'sd', dpar = 'muinfreqcompetitor'),
#   prior(student_t(3, 0, 2), class = 'b', dpar = 'muinfreqcompetitor'),
#   prior(student_t(3, 0, 2), class = 'Intercept', dpar = 'muinfreq'),
#   prior(student_t(3, 0, 2), class = 'sd', dpar = 'muinfreq'),
#   prior(student_t(3, 0, 2), class = 'b', dpar = 'muinfreq')
# )

priors_m1 = c(
  prior(student_t(3, 0, 0.5), class = 'Intercept'), #0.5 might seem small, but in logistic regression this is still quite large since a-prior exp(1) = 2.7 is still plausible.
  prior(student_t(3, 0, 0.5), class = 'b'),
  prior(student_t(3, 0, 0.5), class = 'sd'),
  prior(lkj_corr_cholesky(2), class = 'cor'))
  
# 
# 
# m1 = brm(freq_choice ~ pretraining*condition*stem_condition*task + (1 + stem_condition*task|participant) + (pretraining*condition*task|resp_stem),
#          data = data_m1,
#          family = bernoulli(link = 'logit'),
#          iter = 16000, 
#          warmup = 8000,
#          chains = 4,
#          cores = 4,
#          prior = priors_m1,
#          control = list(adapt_delta = 0.98),
#          file = '../Data/model1')

# 
# m1_smaller = brm(freq_choice ~ (pretraining + condition + stem_condition + task)^3 + (1 + stem_condition*task|participant) + (pretraining*condition*task|resp_stem),
#          data = data_m1,
#          family = bernoulli(link = 'logit'),
#          iter = 10000, 
#          warmup = 5000,
#          chains = 4,
#          cores = 4,
#          prior = priors_m1,
#          #control = list(adapt_delta = 0.98),
#          file = '../Data/model1_small')


m1_smaller = brm(freq_choice ~ condition + pretraining + stem_condition + task + task:condition + pretraining:condition + condition:stem_condition + pretraining:stem_condition 
                 + (1 + stem_condition*task|participant) + (pretraining*condition|resp_stem),
         data = data_m1,
         family = bernoulli(link = 'logit'),
         iter = 10000, 
         warmup = 5000,
         chains = 4,
         cores = 4,
         prior = priors_m1,
         #control = list(adapt_delta = 0.98),
         file = '../Data/model1_small')

fixef(m1_smaller)
# 
# test = glmer(freq_choice ~ pretraining + condition + stem_condition + task + task:condition + pretraining:condition + condition:stem_condition + pretraining:stem_condition 
#                  + (1 + stem_condition*task|participant) + (pretraining*condition|resp_stem),
#          data = data_m1,
#          family = "binomial")




m1_only_familiar_stems = brm(freq_choice ~ pretraining*condition*task + (1 + task|participant) + (pretraining*condition*task|resp_stem),
         data = data_familiar,
         family = bernoulli(link = 'logit'),
         iter = 18000, 
         warmup = 10000,
         chains = 4,
         cores = 4,
         prior = priors_m1,
         control = list(adapt_delta = 0.99),
         file = '../Data/model_familiar')



m1_only_novel_stems = brm(freq_choice ~ pretraining*condition*task + (1 + task|participant) + (pretraining*condition*task|resp_stem),
         data = data_novel,
         family = bernoulli(link = 'logit'),
         iter = 18000, 
         warmup = 10000,
         chains = 4,
         cores = 4,
         prior = priors_m1,
         control = list(adapt_delta = 0.99),
         file = '../Data/model_novel')

fixef(m1_only_familiar_stems)
fixef(m1_only_novel_stems)
```

```{r}
plot_model(m1, type = 'int')
```
