---
title: "Generalizability Analysis Script"
author: "Zachary Houghton"
date: "2023-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = F}
library(tidyverse)
library(brms)
```

## Conditions Table

Table1:

|                |            |           |                |            |           |                  |            |           |
|--------|--------|--------|--------|--------|--------|--------|--------|--------|
| **Condition1** | #of tokens | #of types | **Condition2** | #of tokens | #of types | **Condition3**   | #of tokens | #of types |
| dan            | 12         | 12        | dan            | 12         | 3         | dan              | 12         | 12        |
| nem            | 12         | 3         | nem            | 3          | 3         | nem              | 3          | 3         |
| sil            | 6          | 6         | sil            | 6          | 6         | sil              | 6          | 6         |
| shoon          | 6          | 6         | shoon          | 6          | 6         | shoon            | 6          | 6         |
| **Condition4** |            |           | **Condition5** |            |           | **nem language** | #of tokens | #of types |
| dan            | 12         | 3         | dan            | 3          | 3         | dan              | 3          | 3         |
| nem            | 12         | 12        | nem            | 12         | 3         | nem              | 12         | 12        |
| sil            | 6          | 6         | sil            | 6          | 6         | sil              | 6          | 6         |
| shoon          | 6          | 6         | shoon          | 6          | 6         | shoon            | 6          | 6         |

Table2

|               |               |               |               |                 |              |              |              |                |
|--------|:------:|:------:|:------:|:------:|:------:|:------:|:------:|:------:|
| **Condition** | **dan token** | **nem token** | **sil token** | **shoon token** | **dan type** | **nem type** | **sil type** | **shoon type** |
| 1             |      12       |      12       |       6       |        6        |      12      |      3       |      6       |       6        |
| 2             |      12       |       3       |       6       |        6        |      3       |      3       |      6       |       6        |
| 3             |      12       |       3       |       6       |        6        |      12      |      3       |      6       |       6        |
| 4             |      12       |      12       |       6       |        6        |      3       |      12      |      6       |       6        |
| 5             |       3       |      12       |       6       |        6        |      3       |      3       |      6       |       6        |
| 6             |       3       |      12       |       6       |        6        |      3       |      12      |      6       |       6        |

## Data Preparation

First let's load our data and clean it up

```{r message = F}
data = read_csv('Database_AllParticipants_generalizability_331068_2023-10-17_22h20.54_9982e361-5ad6-4ca4-aeb4-8dad31e0daef.csv')

data_analysis = data %>%
  dplyr::select(participant, date, condition, pretraining, textbox.text, textbox_5.text, textbox_6.text, prod_label, prod_condition, prod_image2, prod_resp.text, key_resp_16.keys, comp_label1_location, comp_label2_location, label1, label2, comp_condition_stem, comp_condition_suffix, stem) %>%
  rename(age = textbox.text,
         native_lang = textbox_5.text,
         other_langs = textbox_6.text,
         fc_resp = key_resp_16.keys,
         fc_label1_location = comp_label1_location,
         fc_label2_location = comp_label2_location,
         fc_label1 = label1,
         fc_label2 = label2,
         prod_suffix = prod_image2,
         fc_condition_stem = comp_condition_stem,
         fc_condition_suffix = comp_condition_suffix,
         prod_resp = prod_resp.text,
         prod_stem = prod_label,
         resp_stem = stem) %>%
  group_by(participant) %>%
  fill(c(condition, pretraining, age, native_lang, other_langs)) 

data_analysis$date = gsub('_.*', '', data_analysis$date)
data_analysis$date = as.Date(data_analysis$date)

data_analysis = data_analysis %>%
  filter(date > '2023-10-11')

data_analysis$pretraining = as.factor(data_analysis$pretraining / 100)
data_analysis$condition = as.factor(data_analysis$condition)
data_analysis = data_analysis %>%
  mutate(fc_condition_suffix = ifelse(fc_condition_suffix == 'big', 'big_pl', fc_condition_suffix))

data_analysis_2afc = data_analysis %>%
  select(participant, date, condition, pretraining, age, native_lang, other_langs, fc_resp, fc_label1_location, fc_label2_location, fc_label1, fc_label2, fc_condition_stem, fc_condition_suffix, resp_stem) %>%
  drop_na(fc_resp)

data_analysis_prod = data_analysis %>%
  select(participant, date, condition, pretraining, age, native_lang, other_langs, prod_stem, prod_suffix, prod_condition, prod_resp) %>%
  drop_na(prod_resp)

data_analysis_prod$prod_suffix = gsub('.*/[0-9]*_(.+)\\.PNG', '\\1', data_analysis_prod$prod_suffix)

data_analysis_prod$prod_suffix[data_analysis_prod$prod_suffix=='2'] = 'big_pl'

data_analysis_prod = data_analysis_prod %>%
  mutate(prod_resp_suffix = str_extract_all(prod_resp, 'dan|sil|shoon|nem'))

data_analysis_2afc = data_analysis_2afc %>%
  mutate(resp = ifelse(fc_resp == fc_label1_location, fc_label1, fc_label2))

data_analysis_2afc = data_analysis_2afc %>%
  mutate(resp_suffix = str_extract_all(resp, 'dan|sil|shoon|nem'))

data_analysis_2afc = data_analysis_2afc %>%
  mutate(freq_choice = ifelse(condition %in% c(1,2,3), 
                              ifelse(resp_suffix == 'dan', 'freq',
                              ifelse(resp_suffix == 'sil', 'freq_competitor',
                              ifelse(resp_suffix == 'nem', 'infreq', 'infreq_competitor'))),
         ifelse(resp_suffix == 'nem', 'freq', #if condition is 4,5, or 6
         ifelse(resp_suffix == 'dan', 'infreq',
         ifelse(resp_suffix == 'shoon', 'freq_competitor', 'infreq_competitor')))))


data_analysis_prod = data_analysis_prod %>%
  mutate(freq_choice = ifelse(condition %in% c(1,2,3), 
                              ifelse(prod_resp_suffix == 'dan', 'freq',
                              ifelse(prod_resp_suffix == 'sil', 'freq_competitor',
                              ifelse(prod_resp_suffix == 'nem', 'infreq', 'infreq_competitor'))),
         ifelse(prod_resp_suffix == 'nem', 'freq', #if condition is 4,5, or 6
         ifelse(prod_resp_suffix == 'dan', 'infreq',
         ifelse(prod_resp_suffix == 'shoon', 'freq_competitor', 'infreq_competitor')))))

names = c('resp_stem', 'picture_meaning', 'stem_condition', 'resp', 'resp_suffix_form')
names_2afc = c('stem_condition', 'picture_meaning', 'resp_stem', 'resp', 'resp_suffix_form')

colnames(data_analysis_prod)[8:12] = names
colnames(data_analysis_2afc)[13:17] = names_2afc



data_analysis_2afc = data_analysis_2afc %>%
  select(participant, date, condition, pretraining, age, native_lang, other_langs, stem_condition, picture_meaning, resp_stem, resp, resp_suffix_form, freq_choice) %>%
  mutate(task = '2afc')

data_analysis_prod = data_analysis_prod %>%
  mutate(task = 'prod')

data_analysis = data_analysis_2afc %>%
  full_join(data_analysis_prod)
```

```{r}
data_analysis = data_analysis %>%
  mutate(meaning_choice = ifelse(condition %in% c(1,2,3), 
                              ifelse(picture_meaning == 'big_pl', 'freq',
                              ifelse(picture_meaning == 'dim_sg', 'infreq', 'novel')),
         ifelse(picture_meaning == 'big_pl', 'infreq', #if condition is 4,5, or 6
         ifelse(picture_meaning == 'dim_sg', 'freq', 'novel'))))
```

# Analysis

Our dependent measure will be `freq_choice`.

Our independent measures will be pretraining, condition, stem_condition (whether the stem was familiar or novel), and task

<!--# add predictions? -->

<!--# analyses: freq_choice ~ pretraining*condition*stem_condition*task + (1|stem) + (1 + stem_condition*task|participant) + (pretraining*condition*task|stem) -->

<!--# freq vs infreq for novel meanings -->

<!--# freq vs freq competitor for novel meanings -->

<!--# change condition coding (dan and nem should be collapsed, should 4,5,6 should be 1,2,3 -->

<!--# also add analyses for subset data, subsetting by stem_condition and picture_meaning -->
