---
title: "Generalizability Analysis"
author: "Zachary Houghton"
date: "2023-10-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(brms)
library(sjPlot)
library(dplyr)
library(future)
library(future.apply)
options(contrasts = c("contr.sum", "contr.sum"))

# On a 28-core machine: 7 concurrent models × 4 cores each = 28 cores fully utilized.
# Workers are separate R sessions, so brms/Stan threading within each is independent.
plan(multisession, workers = min(7L, (parallel::detectCores() - 4L) %/% 4L))

# Absolute path used inside future workers (relative paths break across sessions)
DATA_DIR <- normalizePath('../Data')

# ── Convergence logging ───────────────────────────────────────────────────────
# After fitting each model, call log_convergence() to record Rhat / ESS issues.
# Re-run flagged models after inspecting the log at DATA_DIR/convergence_log.csv.
log_convergence <- function(model, model_name,
                            log_path = file.path(DATA_DIR, 'convergence_log.csv')) {
  s        <- summary(model)
  all_pars <- rbind(
    as.data.frame(s$fixed),
    if (!is.null(s$random)) do.call(rbind, lapply(s$random, as.data.frame)) else data.frame()
  )
  rhats <- all_pars$Rhat;  bulk <- all_pars$Bulk_ESS;  tail <- all_pars$Tail_ESS
  issues <- character(0)
  bad_rhat <- rownames(all_pars)[!is.na(rhats) & rhats > 1.01]
  bad_bulk <- rownames(all_pars)[!is.na(bulk)  & bulk  < 400]
  bad_tail <- rownames(all_pars)[!is.na(tail)  & tail  < 400]
  if (length(bad_rhat) > 0) issues <- c(issues, paste0("Rhat>1.01[",      paste(bad_rhat, collapse=","), "]"))
  if (length(bad_bulk) > 0) issues <- c(issues, paste0("low_bulk_ESS[",   paste(bad_bulk, collapse=","), "]"))
  if (length(bad_tail) > 0) issues <- c(issues, paste0("low_tail_ESS[",   paste(bad_tail, collapse=","), "]"))

  entry <- data.frame(model     = model_name,
                      status    = if (length(issues) == 0) "OK" else paste(issues, collapse = "; "),
                      timestamp = format(Sys.time()),
                      stringsAsFactors = FALSE)

  if (file.exists(log_path)) {
    existing <- read.csv(log_path, stringsAsFactors = FALSE)
    if (model_name %in% existing$model) {
      existing[existing$model == model_name, ] <- entry
    } else {
      existing <- rbind(existing, entry)
    }
    write.csv(existing, log_path, row.names = FALSE)
  } else {
    write.csv(entry, log_path, row.names = FALSE)
  }

  if (length(issues) > 0)
    message(sprintf("WARNING — %s: %s", model_name, paste(issues, collapse = "; ")))
  invisible(model)
}
```

## Conditions Table

|   | Frequent Token | Frequent Type | Infrequent Token | Infrequent Type |
|---|---|---|---|---|
| **Condition 1** | 12 | 12 | 12 | 3 |
| **Condition 2** | 12 | 3  | 3  | 3 |
| **Condition 3** | 12 | 12 | 3  | 3 |

Conditions 4–6 mirror 1–3 with the dan/nem roles swapped (nem is the high-frequency suffix).

---

# Data Preparation

```{r load-data, message=FALSE}
data <- read.csv('../Data/data.csv', quote = '"')

data_analysis <- data %>%
  dplyr::select(participant, date, condition, textbox.text, textbox_5.text, textbox_6.text,
                prod_label, prod_condition, prod_image2, prod_resp.text, key_resp_16.keys,
                comp_label1_location, comp_label2_location, label1, label2,
                comp_condition_stem, comp_condition_suffix, stem, stem_condition,
                mouse.clicked_name, comprehension_label, suffix) %>%
  rename(age                = textbox.text,
         native_lang        = textbox_5.text,
         other_langs        = textbox_6.text,
         fc_resp            = key_resp_16.keys,
         fc_label1_location = comp_label1_location,
         fc_label2_location = comp_label2_location,
         fc_label1          = label1,
         fc_label2          = label2,
         prod_suffix        = prod_image2,
         fc_condition_stem  = comp_condition_stem,
         fc_condition_suffix= comp_condition_suffix,
         prod_resp          = prod_resp.text,
         prod_stem          = prod_label,
         resp_stem          = stem) %>%
  mutate(comprehension_response = case_when(
    mouse.clicked_name == 'prod_image1_5' ~ 'big_sg',
    mouse.clicked_name == 'prod_image2_3' ~ 'dim_sg',
    mouse.clicked_name == 'alt_image1_3'  ~ 'dim_pl',
    mouse.clicked_name == 'alt_image2_3'  ~ 'big_pl'
  )) %>%
  group_by(participant) %>%
  fill(c(condition, age, native_lang, other_langs))
# NOTE: data_analysis is still grouped by participant after fill(); this
# propagates through later joins and makes filter(!any(...)) work per-participant.

data_analysis$date      <- gsub('_.*', '', data_analysis$date)
data_analysis$date      <- as.Date(data_analysis$date)
data_analysis           <- data_analysis %>% filter(date > '2024-10-01')
data_analysis$condition <- as.factor(data_analysis$condition)
data_analysis           <- data_analysis %>%
  mutate(fc_condition_suffix = ifelse(fc_condition_suffix == 'big', 'big_pl', fc_condition_suffix))
```

```{r split-tasks}
data_analysis_2afc <- data_analysis %>%
  select(participant, date, condition, age, native_lang, other_langs,
         fc_resp, fc_label1_location, fc_label2_location, fc_label1, fc_label2,
         fc_condition_stem, fc_condition_suffix, resp_stem) %>%
  drop_na(fc_resp)

data_analysis_prod <- data_analysis %>%
  select(participant, date, condition, age, native_lang, other_langs,
         prod_stem, prod_suffix, prod_condition, prod_resp) %>%
  drop_na(prod_resp)

data_analysis_prod$prod_suffix <- gsub('.*/[0-9]*_(.+)\\.PNG', '\\1', data_analysis_prod$prod_suffix)
data_analysis_prod$prod_suffix[data_analysis_prod$prod_suffix == '2'] <- 'big_pl'

data_analysis_comprehension <- data_analysis %>%
  select(participant, date, condition, age, native_lang, other_langs,
         stem_condition, comprehension_label, comprehension_response)
```

```{r bad-participants}
bad_participants <- c(21648, 942255, 649741, 813027, 153394, 644767, 839046, 291576, 549825, 317268,
                      510986, 329047, 932850, 164814, 957856, 22470, 897907, 961820, 770478, 314909,
                      309918, 127245, 503226, 896045, 300947, 66695, 166035, 273572, 732396, 737249,
                      26157, 630864, 692114, 997216, 211393, 943399, 353750, 237361, 57092, 846859,
                      77553, 886837,
                      # added 2026-07-18: heavy omitters (>33%) from production typo classifier
                      10491, 15520, 82399, 84071, 125083, 147644, 174426, 181275, 204118, 259690,
                      272267, 342213, 343203, 350678, 375011, 385370, 415922, 419006, 437854, 450045,
                      450726, 470882, 519471, 520100, 530171, 574111, 600966, 617987, 649153, 661435,
                      680109, 751078, 763736, 764107, 766408, 780425, 784894, 787582, 805133, 822862,
                      828476, 849639, 900759, 914846, 981477)
# participant column is character (due to hex ID in data.csv); cast to integer for matching
```

```{r join-prod-classified}
prod_classified_df <- read.csv('../Data/prod_classified.csv', stringsAsFactors = FALSE) %>%
  dplyr::select(participant, stem, resp, corrected_suffix, combination) %>%
  dplyr::rename(prod_stem = stem, prod_resp = resp)
# Keep participant as character to match data_analysis_prod$participant type

data_analysis_prod <- data_analysis_prod %>%
  filter(!as.integer(participant) %in% bad_participants)

data_analysis_prod <- data_analysis_prod %>%
  left_join(prod_classified_df, by = c('participant', 'prod_stem', 'prod_resp')) %>%
  filter(combination == 0 | is.na(combination)) %>%
  mutate(prod_resp_suffix = corrected_suffix) %>%
  dplyr::select(-corrected_suffix, -combination) %>%
  mutate(language = case_when(condition %in% c(1,2,3) ~ 'dan', condition %in% c(4,5,6) ~ 'nem'))

data_analysis_prod$condition <- factor(data_analysis_prod$condition)
data_analysis_prod$date      <- as.Date(as.character(data_analysis_prod$date))
```

```{r filter-2afc-comprehension}
data_analysis_comprehension <- data_analysis_comprehension %>%
  mutate(comprehension_suffix = str_extract_all(comprehension_label, 'dan|sil|shoon|nem')) %>%
  unnest(comprehension_suffix, keep_empty = TRUE) %>%
  mutate(language = case_when(condition %in% c(1,2,3) ~ 'dan', condition %in% c(4,5,6) ~ 'nem')) %>%
  filter(!as.integer(participant) %in% bad_participants)

data_analysis_2afc <- data_analysis_2afc %>%
  mutate(resp = ifelse(fc_resp == fc_label1_location, fc_label1, fc_label2)) %>%
  filter(!as.integer(participant) %in% bad_participants)

data_analysis_2afc <- data_analysis_2afc %>%
  mutate(resp_suffix = str_extract_all(resp, 'dan|sil|shoon|nem')) %>%
  unnest(resp_suffix, keep_empty = TRUE)

data_analysis_2afc <- data_analysis_2afc %>%
  mutate(accuracy = case_when(
    fc_condition_suffix == 'big_pl' ~ ifelse(resp_suffix %in% c('dan', 'sil'), 1, 0),
    fc_condition_suffix == 'dim_sg' ~ ifelse(resp_suffix %in% c('nem', 'shoon'), 1, 0))) %>%
  mutate(language = case_when(condition %in% c(1,2,3) ~ 'dan', condition %in% c(4,5,6) ~ 'nem'))
```

```{r freq-choice}
data_analysis_2afc <- data_analysis_2afc %>%
  mutate(freq_choice = ifelse(condition %in% c(1,2,3),
    ifelse(resp_suffix == 'dan', 'freq',
    ifelse(resp_suffix == 'sil', 'freq_competitor',
    ifelse(resp_suffix == 'nem', 'infreq', 'infreq_competitor'))),
    ifelse(resp_suffix == 'nem', 'freq',
    ifelse(resp_suffix == 'dan', 'infreq',
    ifelse(resp_suffix == 'shoon', 'freq_competitor', 'infreq_competitor')))))

data_analysis_prod <- data_analysis_prod %>%
  mutate(freq_choice = ifelse(condition %in% c(1,2,3),
    ifelse(prod_resp_suffix == 'dan', 'freq',
    ifelse(prod_resp_suffix == 'sil', 'freq_competitor',
    ifelse(prod_resp_suffix == 'nem', 'infreq', 'infreq_competitor'))),
    ifelse(prod_resp_suffix == 'nem', 'freq',
    ifelse(prod_resp_suffix == 'dan', 'infreq',
    ifelse(prod_resp_suffix == 'shoon', 'freq_competitor', 'infreq_competitor')))))

data_analysis_comprehension <- data_analysis_comprehension %>%
  mutate(freq_choice = ifelse(condition %in% c(1,2,3),
    ifelse(comprehension_suffix == 'dan', 'freq',
    ifelse(comprehension_suffix == 'sil', 'freq_competitor',
    ifelse(comprehension_suffix == 'nem', 'infreq', 'infreq_competitor'))),
    ifelse(comprehension_suffix == 'nem', 'freq',
    ifelse(comprehension_suffix == 'dan', 'infreq',
    ifelse(comprehension_suffix == 'shoon', 'freq_competitor', 'infreq_competitor')))))
```

```{r rename-columns}
names      <- c('resp_stem', 'picture_meaning', 'stem_condition', 'resp', 'resp_suffix_form')
names_2afc <- c('stem_condition', 'picture_meaning', 'resp_stem', 'resp', 'resp_suffix_form')
colnames(data_analysis_prod)[7:11]  <- names
colnames(data_analysis_2afc)[12:16] <- names_2afc

data_analysis_prod <- data_analysis_prod %>%
  mutate(accuracy = case_when(
    picture_meaning == 'big_pl' ~ ifelse(resp_suffix_form %in% c('dan', 'sil'), 1, 0),
    picture_meaning == 'dim_sg' ~ ifelse(resp_suffix_form %in% c('nem', 'shoon'), 1, 0)))

data_analysis_2afc <- data_analysis_2afc %>%
  select(participant, date, condition, age, native_lang, other_langs,
         stem_condition, picture_meaning, resp_stem, resp, resp_suffix_form,
         freq_choice, accuracy, language) %>%
  mutate(task = '2afc')

data_analysis_prod <- data_analysis_prod %>%
  mutate(task = 'prod')

data_analysis_prod$condition <- factor(data_analysis_prod$condition)
```

```{r join-tasks}
data_analysis <- data_analysis_2afc %>%
  full_join(data_analysis_prod)
# data_analysis inherits grouping by participant from data_analysis_2afc

accuracy_scores <- data_analysis %>%
  filter(task == '2afc') %>%
  group_by(participant) %>%
  summarize(mean_accuracy = mean(accuracy, na.rm = TRUE),
            sd_accuracy   = sd(accuracy,   na.rm = TRUE))

# Remove non-English native language participants (group-level: removes entire participant)
data_analysis <- data_analysis %>%
  filter(!any(native_lang %in% c('Spanish\n', 'Vietnames', 'Vietnames\n', 'hebrew\n')))

cat("Final N:", length(unique(data_analysis$participant)), "\n")
data_analysis %>%
  filter(!is.na(condition)) %>%
  distinct(participant, condition) %>%
  count(condition) %>%
  arrange(condition)
```

```{r finalize-data}
data_analysis <- data_analysis %>%
  mutate(meaning_choice = ifelse(condition %in% c(1,2,3),
    ifelse(picture_meaning == 'big_pl', 'freq',
    ifelse(picture_meaning == 'dim_sg', 'infreq', 'novel')),
    ifelse(picture_meaning == 'big_pl', 'infreq',
    ifelse(picture_meaning == 'dim_sg', 'freq', 'novel')))) %>%
  mutate(language = case_when(
    condition %in% c(1,2,3) ~ 'dan',
    condition %in% c(4,5,6) ~ 'nem')) %>%
  mutate(original_condition = condition) %>%
  # Fold conditions 4-6 onto 1-3 (nem language mirrors dan language structure)
  mutate(condition = ifelse(condition == 4, 1,
                    ifelse(condition == 5, 2,
                    ifelse(condition == 6, 3, condition)))) %>%
  filter(!is.na(resp_suffix_form)) %>%
  left_join(accuracy_scores, by = 'participant')

# Comprehension: fold conditions and clean
data_analysis_comprehension <- data_analysis_comprehension %>%
  filter(!is.na(comprehension_response)) %>%
  select(-freq_choice) %>%
  mutate(comprehension_suffix = case_when(
    is.na(comprehension_suffix)  ~ 'none',
    !is.na(comprehension_suffix) ~ comprehension_suffix)) %>%
  mutate(condition = ifelse(condition == 4, 1,
                    ifelse(condition == 5, 2,
                    ifelse(condition == 6, 3, condition))))
```

---

# Human Experiment Analysis

## Statistical Models for Paper

Models run in parallel (7 concurrent × 4 cores each = 28 cores).
Convergence issues are logged to `../Data/convergence_log.csv`.

### Prep Data

```{r paper-prep}
options(contrasts = c("contr.treatment", "contr.treatment"))

data_prod <- data_analysis %>%
  filter(task == 'prod') %>%
  filter(resp_suffix_form %in% c('dan', 'nem'))

data_2afc <- data_analysis %>%
  filter(task == '2afc') %>%
  filter(resp_suffix_form %in% c('dan', 'nem'))

# Production: keep accuracy==1 (correct meaning) or NA (novel meaning, no correct answer)
data_prod_no_sil_shoon <- data_prod %>%
  mutate(
    meaning   = case_when(
      picture_meaning %in% c('big_pl', 'dim_sg') ~ 'original',
      picture_meaning == 'dim_pl'                ~ 'novel'),
    frequency = case_when(
      freq_choice == 'freq'   ~ 1,
      freq_choice == 'infreq' ~ 0,
      .default = NA)) %>%
  filter((accuracy == 1) %>% replace_na(TRUE))

data_2afc <- data_2afc %>%
  filter(resp_suffix_form %in% c('dan', 'nem')) %>%
  mutate(
    meaning   = case_when(
      picture_meaning %in% c('big_pl', 'dim_sg') ~ 'original',
      picture_meaning == 'dim_pl'                ~ 'novel'),
    frequency = case_when(
      freq_choice == 'freq'   ~ 1,
      freq_choice == 'infreq' ~ 0,
      .default = NA)) %>%
  filter((accuracy == 1) %>% replace_na(TRUE))

data_prod_no_sil_shoon$participant <- factor(data_prod_no_sil_shoon$participant)
data_prod_no_sil_shoon$condition   <- factor(data_prod_no_sil_shoon$condition, levels = c(3, 1, 2))
data_2afc$condition                <- factor(data_2afc$condition, levels = c(3, 1, 2))

write_csv(data_prod_no_sil_shoon, '../Data/data_prod_no_sil_shoon.csv')

# Split by meaning
data_prod_original              <- data_prod_no_sil_shoon %>% filter(meaning == 'original')
data_prod_original_cond2_baseline <- data_prod_original  %>% mutate(condition = factor(condition, levels = c('2','1','3')))
data_prod_novel                 <- data_prod_no_sil_shoon %>% filter(meaning == 'novel')
data_prod_novel_cond2_baseline  <- data_prod_novel        %>% mutate(condition = factor(condition, levels = c('2','1','3')))

data_2afc_original              <- data_2afc %>% filter(meaning == 'original')
data_2afc_original_cond2_baseline <- data_2afc_original  %>% mutate(condition = factor(condition, levels = c('2','1','3')))
data_2afc_novel                 <- data_2afc %>% filter(meaning == 'novel')
data_2afc_novel_cond2_baseline  <- data_2afc_novel        %>% mutate(condition = factor(condition, levels = c('2','1','3')))

data_prod_both      <- data_prod_original %>% full_join(data_prod_novel)
data_prod_both$meaning        <- factor(data_prod_both$meaning)
contrasts(data_prod_both$meaning)        <- contr.sum(levels(data_prod_both$meaning))
data_prod_both$stem_condition <- factor(data_prod_both$stem_condition, levels = c('novel','familiar'))
contrasts(data_prod_both$stem_condition) <- contr.sum(levels(data_prod_both$stem_condition))

data_2afc_both      <- data_2afc_original %>% full_join(data_2afc_novel)
data_2afc_both$meaning        <- factor(data_2afc_both$meaning)
contrasts(data_2afc_both$meaning)        <- contr.sum(levels(data_2afc_both$meaning))
data_2afc_both$stem_condition <- factor(data_2afc_both$stem_condition)
contrasts(data_2afc_both$stem_condition) <- contr.sum(levels(data_2afc_both$stem_condition))

data_2afc_both$participant <- factor(data_2afc_both$participant)
data_prod_2afc_both <- data_2afc_both %>% full_join(data_prod_both)
data_prod_2afc_both$meaning        <- factor(data_prod_2afc_both$meaning,        levels = c('novel','original'))
contrasts(data_prod_2afc_both$meaning)        <- contr.sum(levels(data_prod_2afc_both$meaning))
data_prod_2afc_both$stem_condition <- factor(data_prod_2afc_both$stem_condition, levels = c('novel','familiar'))
contrasts(data_prod_2afc_both$stem_condition) <- contr.sum(levels(data_prod_2afc_both$stem_condition))
data_prod_2afc_both$task <- factor(data_prod_2afc_both$task)
contrasts(data_prod_2afc_both$task) <- contr.sum(levels(data_prod_2afc_both$task))

# Comprehension prep
data_analysis_comprehension <- data_analysis_comprehension %>%
  mutate(
    freq_suffix    = case_when(
      language == 'dan' & comprehension_suffix == 'dan' ~ 'freq',
      language == 'nem' & comprehension_suffix == 'nem' ~ 'freq',
      .default = 'infreq'),
    original_meaning = case_when(
      comprehension_suffix == 'dan' & comprehension_response == 'big_pl' ~ 1,
      comprehension_suffix == 'nem' & comprehension_response == 'dim_sg' ~ 1,
      .default = 0),
    novel_meaning = case_when(
      comprehension_suffix %in% c('dan','nem') & comprehension_response == 'dim_pl' ~ 1,
      .default = 0)) %>%
  filter(novel_meaning == 1 | original_meaning == 1) %>%
  mutate(
    frequent = case_when(
      language == 'dan' & comprehension_suffix == 'dan' ~ 1,
      language == 'nem' & comprehension_suffix == 'nem' ~ 1,
      .default = 0),
    meaning = case_when(
      comprehension_suffix == 'dan' & comprehension_response == 'big_pl' ~ 'original',
      comprehension_suffix == 'nem' & comprehension_response == 'dim_sg' ~ 'original',
      comprehension_response == 'dim_pl'                                 ~ 'novel',
      .default = NA))

data_analysis_comprehension$frequent  <- factor(data_analysis_comprehension$frequent)
data_analysis_comprehension$condition <- factor(data_analysis_comprehension$condition, levels = c(3, 1, 2))
data_analysis_comprehension           <- data_analysis_comprehension %>%
  mutate(meaning = case_when(meaning == 'novel' ~ 1, meaning == 'original' ~ 0))
data_analysis_comprehension$meaning <- factor(data_analysis_comprehension$meaning)

data_analysis_comprehension$language <- factor(data_analysis_comprehension$language)
contrasts(data_analysis_comprehension$language) <- contr.sum(levels(data_analysis_comprehension$language))

data_analysis_comprehension_cond2_baseline <- data_analysis_comprehension %>%
  mutate(condition = factor(condition, levels = c('2','1','3')))

options(contrasts = c('contr.treatment', 'contr.treatment'))

data_analysis_comprehension <- data_analysis_comprehension %>%
  mutate(
    frequency = ifelse(comprehension_suffix == language, 1, 0),
    condition_numeric = case_when(
      (condition == '1' & frequency == 1) | (condition == '3' & frequency == 1) ~ '12-12',
      (condition == '1' & frequency == 0) | (condition == '2' & frequency == 1) ~ '12-3',
      (condition == '2' & frequency == 0) | (condition == '3' & frequency == 0) ~ '3-3'))

data_analysis_comprehension$condition_numeric <- factor(data_analysis_comprehension$condition_numeric,
                                                        levels = c('12-3', '12-12', '3-3'))
data_analysis_comprehension$stem_condition    <- factor(data_analysis_comprehension$stem_condition)
contrasts(data_analysis_comprehension$stem_condition) <- contr.sum(levels(data_analysis_comprehension$stem_condition))

write_csv(data_analysis_comprehension, '../Data/data_analysis_comprehension.csv')
```

### Production

```{r priors-prod}
priors_prod <- c(
  prior(student_t(3, 0, 1), class = 'Intercept'),
  prior(student_t(3, 0, 1), class = 'b'),
  prior(student_t(3, 0, 1), class = 'sd'))
```

```{r production-models}
# ── Launch all production models in parallel ──────────────────────────────────
f_prod_original <- future({
  brm(frequency ~ condition + (1 | participant),
      data = data_prod_original, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_prod, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_prod_original'))
})

f_prod_novel <- future({
  brm(frequency ~ condition + (1 | participant),
      data = data_prod_novel, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_prod, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_prod_novel'))
})

f_prod_both <- future({
  brm(frequency ~ condition*meaning + (1 + meaning | participant),
      data = data_prod_both, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_prod, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_prod_both'))
})

f_prod_both_stem <- future({
  brm(frequency ~ condition*meaning*stem_condition + (1 + meaning*stem_condition | participant) + (1 | resp_stem),
      data = data_prod_both, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_prod, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_prod_both_stem'))
})

f_prod_original_cond2 <- future({
  brm(frequency ~ condition + (1 | participant) + (condition | resp_stem),
      data = data_prod_original_cond2_baseline, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_prod, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_prod_original_cond2_baseline'))
})

f_prod_novel_cond2 <- future({
  brm(frequency ~ condition + (1 | participant) + (condition | resp_stem),
      data = data_prod_novel_cond2_baseline, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_prod, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_prod_novel_cond2_baseline'))
})

# Collect
model_prod_original          <- value(f_prod_original)
model_prod_novel             <- value(f_prod_novel)
model_prod_both              <- value(f_prod_both)
model_prod_both_stem         <- value(f_prod_both_stem)
model_prod_original_cond2_baseline <- value(f_prod_original_cond2)
model_prod_novel_cond2_baseline    <- value(f_prod_novel_cond2)
```

```{r production-results}
fixef(model_prod_original)
fixef(model_prod_novel)

hypothesis(model_prod_original, "-c(condition1 + condition2) = 0")
hypothesis(model_prod_novel,    "-c(condition1 + condition2) = 0")

percent_greater_zero_original <- data.frame(fixef(model_prod_original, summary = FALSE)) %>%
  pivot_longer(cols = everything(), names_to = 'beta_coefficient', values_to = 'estimate') %>%
  group_by(beta_coefficient) %>%
  summarize(pct_gt_zero = sum(estimate > 0) / n() * 100)

percent_greater_zero_original_cond3 <- data.frame(fixef(model_prod_original, summary = FALSE)) %>%
  summarize(pct = sum(condition1 + condition2 > 0) / n() * 100, n = n())

percent_greater_zero_novel <- data.frame(fixef(model_prod_novel, summary = FALSE)) %>%
  pivot_longer(cols = everything(), names_to = 'beta_coefficient', values_to = 'estimate') %>%
  group_by(beta_coefficient) %>%
  summarize(pct_gt_zero = sum(estimate > 0) / n() * 100)

percent_greater_zero_novel_cond3 <- data.frame(fixef(model_prod_novel, summary = FALSE)) %>%
  summarize(pct = sum(condition1 + condition2 > 0) / n() * 100, n = n())

percent_greater_zero_original
percent_greater_zero_novel

plot_prod_stem <- plot_model(model_prod_both_stem, type = 'int',
                             axis.title  = c('Condition', 'Frequency'),
                             legend.title = 'Meaning',
                             title = "", dot.size = 2, line.size = 1,
                             colors = c('#298c8c', '#800074'))[[4]]
plot_prod_stem$data$group_col <- factor(plot_prod_stem$data$group_col, levels = c('novel','original'), labels = c('Novel','Original'))
plot_prod_stem$data$group     <- factor(plot_prod_stem$data$group,     levels = c('novel','original'), labels = c('Novel','Original'))
plot_prod_stem$data$facet     <- factor(plot_prod_stem$data$facet,     levels = c('novel','familiar'), labels = c('Novel','Familiar'))
plot_prod_stem +
  labs(linetype = 'Meaning', shape = 'Meaning') +
  scale_x_continuous(breaks = c(1,2,3),
                     labels = c('Type Frequency','Token Frequency','Type-Token Frequency')) +
  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

log_convergence(model_prod_original,          "model_prod_original")
log_convergence(model_prod_novel,             "model_prod_novel")
log_convergence(model_prod_both,              "model_prod_both")
log_convergence(model_prod_both_stem,         "model_prod_both_stem")
log_convergence(model_prod_original_cond2_baseline, "model_prod_original_cond2_baseline")
log_convergence(model_prod_novel_cond2_baseline,    "model_prod_novel_cond2_baseline")
```

### 2AFC

```{r priors-2afc}
priors_2afc <- c(
  prior(student_t(3, 0, 0.5), class = 'Intercept'),
  prior(student_t(3, 0, 0.5), class = 'b'),
  prior(student_t(3, 0, 0.5), class = 'sd'))
```

```{r 2afc-models}
f_2afc_original <- future({
  brm(frequency ~ condition + (1 | participant),
      data = data_2afc_original, family = bernoulli(link = 'logit'),
      iter = 20000, warmup = 10000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_original'))
})

f_2afc_novel <- future({
  brm(frequency ~ condition + (1 | participant),
      data = data_2afc_novel, family = bernoulli(link = 'logit'),
      iter = 30000, warmup = 15000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_novel'))
})

f_2afc_both <- future({
  brm(frequency ~ condition*meaning + (1 + meaning | participant),
      data = data_2afc_both, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_both'))
})

f_2afc_both_stem_dif_cond <- future({
  data_2afc_both_dc <- data_2afc_both
  data_2afc_both_dc$condition_diff <- factor(data_2afc_both_dc$condition, levels = c(1,2,3))
  brm(frequency ~ condition_diff*meaning*stem_condition + (1 + meaning | participant),
      data = data_2afc_both_dc, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_both_stem_dif_conditions'))
})

f_2afc_both_stem <- future({
  brm(frequency ~ condition*meaning*stem_condition + (1 + meaning | participant),
      data = data_2afc_both, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_both_stem'))
})

f_2afc_original_cond2 <- future({
  brm(frequency ~ condition + (1 | participant) + (condition | resp_stem),
      data = data_2afc_original_cond2_baseline, family = bernoulli(link = 'logit'),
      iter = 20000, warmup = 10000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_original_cond2_baseline'))
})

f_2afc_novel_cond2 <- future({
  brm(frequency ~ condition + (1 | participant) + (condition | resp_stem),
      data = data_2afc_novel_cond2_baseline, family = bernoulli(link = 'logit'),
      iter = 30000, warmup = 15000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_novel_cond2_baseline'))
})

f_2afc_prod_both_stem <- future({
  brm(frequency ~ condition*meaning*stem_condition*task + (1 + meaning*task | participant),
      data = data_prod_2afc_both, family = bernoulli(link = 'logit'),
      iter = 14000, warmup = 7000, chains = 4, cores = 4,
      prior = priors_2afc, control = list(adapt_delta = 0.99), seed = 964,
      file = file.path(DATA_DIR, 'model_2afc_prod_both_stem'))
})

# Collect (in two waves — 7 concurrent max)
model_2afc_original          <- value(f_2afc_original)
model_2afc_novel             <- value(f_2afc_novel)
model_2afc_both              <- value(f_2afc_both)
model_2afc_both_stem_dif_conditions <- value(f_2afc_both_stem_dif_cond)
model_2afc_both_stem         <- value(f_2afc_both_stem)
model_2afc_original_cond2_baseline  <- value(f_2afc_original_cond2)
model_2afc_novel_cond2_baseline     <- value(f_2afc_novel_cond2)
model_2afc_prod_both_stem    <- value(f_2afc_prod_both_stem)
```

```{r 2afc-results}
fixef(model_2afc_original)
fixef(model_2afc_novel)

hypothesis(model_2afc_original, "-c(condition1 + condition2) = 0")
hypothesis(model_2afc_novel,    "-c(condition1 + condition2) = 0")

percent_greater_zero_original_2afc <- data.frame(fixef(model_2afc_original, summary = FALSE)) %>%
  pivot_longer(cols = everything(), names_to = 'beta_coefficient', values_to = 'estimate') %>%
  group_by(beta_coefficient) %>%
  summarize(pct_gt_zero = sum(estimate > 0) / n() * 100)

percent_greater_zero_original_cond3_2afc <- data.frame(fixef(model_2afc_original, summary = FALSE)) %>%
  summarize(pct = sum(condition1 + condition2 > 0) / n() * 100, n = n())

percent_greater_zero_novel_2afc <- data.frame(fixef(model_2afc_novel, summary = FALSE)) %>%
  pivot_longer(cols = everything(), names_to = 'beta_coefficient', values_to = 'estimate') %>%
  group_by(beta_coefficient) %>%
  summarize(pct_gt_zero = sum(estimate > 0) / n() * 100)

percent_greater_zero_novel_cond3_2afc <- data.frame(fixef(model_2afc_novel, summary = FALSE)) %>%
  summarize(pct = sum(condition1 + condition2 > 0) / n() * 100, n = n())

percent_greater_zero_original_2afc
percent_greater_zero_novel_2afc

plot_prod_stem_2afc <- plot_model(model_2afc_both_stem_dif_conditions, type = 'int',
                                  axis.title = c('Condition', 'Frequency'),
                                  legend.title = 'Meaning', title = "",
                                  dot.size = 2, line.size = 1,
                                  colors = c('#298c8c', '#800074'))[[4]]
plot_prod_stem_2afc$data$group_col <- factor(plot_prod_stem_2afc$data$group_col, levels = c('novel','original'), labels = c('Novel','Original'))
plot_prod_stem_2afc$data$group     <- factor(plot_prod_stem_2afc$data$group,     levels = c('novel','original'), labels = c('Novel','Original'))
plot_prod_stem_2afc$data$facet     <- factor(plot_prod_stem_2afc$data$facet,     levels = c('novel','familiar'), labels = c('Novel','Familiar'))
plot_prod_stem_2afc +
  labs(linetype = 'Meaning', shape = 'Meaning') +
  scale_x_continuous(breaks = c(1,2,3),
                     labels = c('Type Frequency','Token Frequency','Type-Token Frequency')) +
  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(c(0,1))

log_convergence(model_2afc_original,                 "model_2afc_original")
log_convergence(model_2afc_novel,                    "model_2afc_novel")
log_convergence(model_2afc_both,                     "model_2afc_both")
log_convergence(model_2afc_both_stem_dif_conditions, "model_2afc_both_stem_dif_conditions")
log_convergence(model_2afc_both_stem,                "model_2afc_both_stem")
log_convergence(model_2afc_original_cond2_baseline,  "model_2afc_original_cond2_baseline")
log_convergence(model_2afc_novel_cond2_baseline,     "model_2afc_novel_cond2_baseline")
log_convergence(model_2afc_prod_both_stem,           "model_2afc_prod_both_stem")
```

### Comprehension

```{r priors-comp}
priors_comp <- c(
  prior(student_t(3, 0, 1), class = 'Intercept'),
  prior(student_t(3, 0, 1), class = 'b'),
  prior(student_t(3, 0, 1), class = 'sd'))
```

```{r comprehension-models}
f_comp <- future({
  brm(meaning ~ condition*frequent + (1 + frequent | participant),
      data = data_analysis_comprehension, family = bernoulli(link = 'logit'),
      iter = 10000, warmup = 5000, chains = 4, cores = 4,
      prior = priors_comp, seed = 964,
      file = file.path(DATA_DIR, 'model_comprehension'))
})

f_comp_cond2 <- future({
  brm(meaning ~ condition*frequent + (1 + frequent | participant),
      data = data_analysis_comprehension_cond2_baseline, family = bernoulli(link = 'logit'),
      iter = 10000, warmup = 5000, chains = 4, cores = 4,
      prior = priors_comp, seed = 964,
      file = file.path(DATA_DIR, 'model_comprehension_cond2_baseline'))
})

f_comp_language <- future({
  brm(meaning ~ condition*frequent*language + (1 + frequent | participant) + (frequent | language),
      data = data_analysis_comprehension, family = bernoulli(link = 'logit'),
      iter = 10000, warmup = 5000, chains = 4, cores = 4,
      prior = priors_comp, seed = 964,
      file = file.path(DATA_DIR, 'model_comprehension_language'))
})

f_comp_numeric <- future({
  brm(meaning ~ condition_numeric + (1 | participant),
      data = data_analysis_comprehension, family = bernoulli(link = 'logit'),
      iter = 10000, warmup = 5000, chains = 4, cores = 4,
      prior = priors_comp, seed = 964,
      file = file.path(DATA_DIR, 'model_comprehension_numeric_test'))
})

f_comp_numeric_stem <- future({
  brm(meaning ~ condition_numeric*stem_condition + (1 + stem_condition | participant),
      data = data_analysis_comprehension, family = bernoulli(link = 'logit'),
      iter = 10000, warmup = 5000, chains = 4, cores = 4,
      prior = priors_comp, seed = 964,
      file = file.path(DATA_DIR, 'model_comprehension_numeric_stem_test2'))
})

# Collect
model_comprehension                <- value(f_comp)
model_comprehension_cond2_baseline <- value(f_comp_cond2)
model_comprehension_language       <- value(f_comp_language)
model_comprehension_numeric        <- value(f_comp_numeric)
model_comprehension_numeric_stem   <- value(f_comp_numeric_stem)
```

```{r comprehension-results}
fixef(model_comprehension)
fixef(model_comprehension_numeric)
fixef(model_comprehension_numeric_stem)

hypothesis(model_comprehension, "-c(condition1 + condition2) = 0")

percent_greater_zero_comprehension <- data.frame(fixef(model_comprehension, summary = FALSE)) %>%
  pivot_longer(cols = everything(), names_to = 'beta_coefficient', values_to = 'estimate') %>%
  group_by(beta_coefficient) %>%
  summarize(pct_gt_zero = sum(estimate > 0) / n() * 100)

percent_greater_zero_comprehension_cond3 <- data.frame(fixef(model_comprehension, summary = FALSE)) %>%
  summarize(pct = sum(condition1 + condition2 > 0) / n() * 100, n = n())

freq_effects <- hypothesis(model_comprehension, c(
  "Intercept = Intercept + frequent1",
  "Intercept + condition1 = Intercept + condition1 + frequent1 + condition1:frequent1",
  "Intercept + condition2 = Intercept + condition2 + frequent1 + condition2:frequent1"))

freq_effects_df <- data.frame(
  term     = freq_effects$hypothesis$Hypothesis,
  estimate = freq_effects$hypothesis$Estimate,
  est.error= freq_effects$hypothesis$Est.Error,
  ci2.5    = freq_effects$hypothesis$CI.Lower,
  ci97.5   = freq_effects$hypothesis$CI.Upper)
freq_effects_df

percent_greater_zero_comprehension

log_convergence(model_comprehension,                "model_comprehension")
log_convergence(model_comprehension_cond2_baseline, "model_comprehension_cond2_baseline")
log_convergence(model_comprehension_language,       "model_comprehension_language")
log_convergence(model_comprehension_numeric,        "model_comprehension_numeric")
log_convergence(model_comprehension_numeric_stem,   "model_comprehension_numeric_stem")
```

## Convergence Summary

```{r convergence-summary}
conv_log <- read.csv(file.path(DATA_DIR, 'convergence_log.csv'), stringsAsFactors = FALSE)
cat("Models with issues:\n")
print(conv_log[conv_log$status != "OK", ])
cat("\nAll models:\n")
print(conv_log[, c("model", "status")])
```

---

# Further Exploration

## Key Diagnostic Models

These simpler models are useful for quick inspection and debugging but are not the primary paper analyses.

```{r diag-priors}
priors_diag <- c(
  prior(student_t(3, 0, 0.5), class = 'Intercept'),
  prior(student_t(3, 0, 0.5), class = 'b'),
  prior(student_t(3, 0, 0.5), class = 'sd'))

data_m1 <- data_analysis %>%
  filter(picture_meaning == 'dim_pl') %>%
  mutate(freq_choice = case_when(freq_choice == 'freq' ~ 1, freq_choice == 'infreq' ~ 0)) %>%
  mutate(condition   = as.factor(condition),
         participant = as.factor(participant))

data_prod_diag <- data_m1 %>% filter(task == 'prod')
data_2afc_diag <- data_m1 %>% filter(task == '2afc')
```

```{r diag-models}
f_diag_prod <- future({
  brm(freq_choice ~ condition + (1 | participant) + (1 | resp_stem),
      data = data_prod_diag, family = bernoulli(link = 'logit'),
      iter = 6000, warmup = 3000, chains = 4, cores = 4,
      prior = priors_diag, seed = 964,
      file = file.path(DATA_DIR, 'm1_prod_main'))
})

f_diag_2afc <- future({
  brm(freq_choice ~ condition + (1 | participant) + (1 | resp_stem),
      data = data_2afc_diag, family = bernoulli(link = 'logit'),
      iter = 6000, warmup = 3000, chains = 4, cores = 4,
      prior = priors_diag, seed = 964,
      file = file.path(DATA_DIR, 'm1_2afc_main'))
})

m1_prod_main <- value(f_diag_prod)
m1_2afc_main <- value(f_diag_2afc)

fixef(m1_prod_main)
fixef(m1_2afc_main)

percent_greater_zero_prod <- data.frame(fixef(m1_prod_main, summary = FALSE)) %>%
  pivot_longer(cols = everything(), names_to = 'beta_coefficient', values_to = 'estimate') %>%
  group_by(beta_coefficient) %>%
  summarize(pct_gt_zero = sum(estimate > 0) / n() * 100)

percent_greater_zero_2afc <- data.frame(fixef(m1_2afc_main, summary = FALSE)) %>%
  pivot_longer(cols = everything(), names_to = 'beta_coefficient', values_to = 'estimate') %>%
  group_by(beta_coefficient) %>%
  summarize(pct_gt_zero = sum(estimate > 0) / n() * 100)

percent_greater_zero_prod
percent_greater_zero_2afc
```

## Exploratory Plots

```{r plot-original-meanings}
library(ggh4x)

data_plot_original <- data_analysis %>%
  filter(task == 'prod', picture_meaning %in% c('big_pl', 'dim_sg')) %>%
  group_by(condition, stem_condition) %>%
  count(freq_choice) %>%
  mutate(Frequency = ifelse(freq_choice %in% c('freq', 'freq_competitor'), 'Frequent', 'Infrequent')) %>%
  group_by(Frequency, condition, stem_condition) %>%
  mutate(proportion = n / sum(n)) %>%
  filter(freq_choice %in% c('freq', 'infreq')) %>%
  mutate(stem_condition = ifelse(stem_condition == 'familiar', 'Familiar', 'Novel'))

ggplot(data_plot_original, aes(x = condition, y = proportion, fill = Frequency)) +
  geom_col(position = "dodge") +
  facet_grid(~stem_condition) +
  theme_bw() +
  ggtitle('Production — original meanings') +
  xlab('Condition') + ylab('Proportion') + ylim(0, 1)
```

```{r plot-novel-meanings}
data_plot_novel <- data_analysis %>%
  filter(task == 'prod', picture_meaning == 'dim_pl') %>%
  group_by(condition, stem_condition) %>%
  count(freq_choice) %>%
  mutate(Frequency = ifelse(freq_choice %in% c('freq', 'freq_competitor'), 'Frequent', 'Infrequent')) %>%
  group_by(Frequency, condition, stem_condition) %>%
  mutate(proportion = n / sum(n)) %>%
  filter(freq_choice %in% c('freq', 'infreq')) %>%
  mutate(stem_condition = ifelse(stem_condition == 'familiar', 'Familiar', 'Novel'))

ggplot(data_plot_novel, aes(x = condition, y = proportion, fill = Frequency)) +
  geom_col(position = "dodge") +
  facet_grid(~stem_condition) +
  theme_bw() +
  ggtitle('Production — novel meaning') +
  xlab('Condition') + ylab('Proportion') + ylim(0, 1)
```

```{r plot-suffix-breakdown}
data_suffix_plot <- data_analysis %>%
  filter(task == 'prod', picture_meaning %in% c('big_pl', 'dim_sg')) %>%
  group_by(picture_meaning, condition, stem_condition, language) %>%
  count(resp_suffix_form) %>%
  mutate(proportion = n / sum(n))

ggplot(data_suffix_plot, aes(x = picture_meaning, y = proportion, fill = resp_suffix_form)) +
  geom_col(position = 'dodge') +
  facet_nested(condition ~ stem_condition + language) +
  theme_bw()
```
