---
title: "Grid Search"
author: "Zachary Houghton"
date: "2025-11-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
source("RescorlaLogistic.R")
library(ndl)
library(arm)
library(furrr)
library(future)
library(progressr)
```

## Condition 1 (dan type): 12 token, 12 type (nem 12 tokens 3 types)

```{r}
cond1 = read_csv('../Conditions/Condition1.csv') 

cond1 = cond1 %>%
  mutate(stem = orthoCoding(stem)) %>%
  mutate(type = case_when(
    suffix == 'dan' | suffix == 'sil' ~ 'big_pl',
    suffix == 'none' ~ 'big_sg',
    suffix == 'nem' | suffix == 'shoon' ~ 'dim_sg'
  ))
  

cond1 = cond1 %>%
  mutate(key = paste0(stem, '_', type))

cond1_key = cond1 %>%
  group_by(key, suffix) %>%
  summarize(frequency = table(key))

colnames(cond1_key) = c('Cues', 'Outcomes', 'Frequency')

data_cond1 = cond1_key %>%
  mutate(Frequency = as.numeric(Frequency) * 5) #%>% 
  #mutate(Cues = paste0("cx_", Cues))

data_cond1 = data_cond1 %>%
  uncount(Frequency) %>%
  mutate(Frequency = 1)

```

## Condition 2 (dan token): 12 tokens, 3 types

```{r}

cond2 = read_csv('../Conditions/Condition2.csv') 
cond2 = cond2 %>%
    mutate(stem = orthoCoding(stem)) %>%
  mutate(type = case_when(
    suffix == 'dan' | suffix == 'sil' ~ 'big_pl',
    suffix == 'none' ~ 'big_sg',
    suffix == 'nem' | suffix == 'shoon' ~ 'dim_sg'
  ))
  

cond2 = cond2 %>%
  mutate(key = paste0(stem, '_', type))

cond2_key = cond2 %>%
  group_by(key, suffix) %>%
  summarize(frequency = table(key))

colnames(cond2_key) = c('Cues', 'Outcomes', 'Frequency')

data_cond2 = cond2_key %>%
  mutate(Frequency = as.numeric(Frequency) * 5)# %>% 
  #mutate(Cues = paste0("cx_", Cues))

data_cond2 = data_cond2 %>%
  uncount(Frequency) %>%
  mutate(Frequency = 1)
```

## Condition 3 (dan type and token): 12 tokens, 12 types (nem 3 tokens, 3 types)

```{r}

cond3 = read_csv('../Conditions/Condition3.csv') 
cond3 = cond3 %>%
    mutate(stem = orthoCoding(stem)) %>%
  mutate(type = case_when(
    suffix == 'dan' | suffix == 'sil' ~ 'big_pl',
    suffix == 'none' ~ 'big_sg',
    suffix == 'nem' | suffix == 'shoon' ~ 'dim_sg'
  ))
  

cond3 = cond3 %>%
  mutate(key = paste0(stem, '_', type))

cond3_key = cond3 %>%
  group_by(key, suffix) %>%
  summarize(frequency = table(key))

colnames(cond3_key) = c('Cues', 'Outcomes', 'Frequency')

data_cond3 = cond3_key %>%
  mutate(Frequency = as.numeric(Frequency) * 5)# %>% 
  #mutate(Cues = paste0("cx_", Cues))


data_cond3 = data_cond3 %>%
  uncount(Frequency) %>%
  mutate(Frequency = 1)
```

## Condition 4 (nem type): 12 token, 12 type (dan 12 token, 3 type)

```{r}

cond4 = read_csv('../Conditions/Condition4.csv') 
cond4 = cond4 %>%
    mutate(stem = orthoCoding(stem)) %>%
  mutate(type = case_when(
    suffix == 'dan' | suffix == 'sil' ~ 'big_pl',
    suffix == 'none' ~ 'big_sg',
    suffix == 'nem' | suffix == 'shoon' ~ 'dim_sg'
  ))
  

cond4 = cond4 %>%
  mutate(key = paste0(stem, '_', type))

cond4_key = cond4 %>%
  group_by(key, suffix) %>%
  summarize(frequency = table(key))

colnames(cond4_key) = c('Cues', 'Outcomes', 'Frequency')

data_cond4 = cond4_key %>%
  mutate(Frequency = as.numeric(Frequency) * 5) 

data_cond4 = data_cond4 %>%
  uncount(Frequency) %>%
  mutate(Frequency = 1)
```

## Condition 5 (nem token): 12 token, 3 types (dan 3 token, 3 type)

```{r}

cond5 = read_csv('../Conditions/Condition5.csv') 
cond5 = cond5 %>%
    mutate(stem = orthoCoding(stem)) %>%
  mutate(type = case_when(
    suffix == 'dan' | suffix == 'sil' ~ 'big_pl',
    suffix == 'none' ~ 'big_sg',
    suffix == 'nem' | suffix == 'shoon' ~ 'dim_sg'
  ))
  

cond5 = cond5 %>%
  mutate(key = paste0(stem, '_', type))

cond5_key = cond5 %>%
  group_by(key, suffix) %>%
  summarize(frequency = table(key))

colnames(cond5_key) = c('Cues', 'Outcomes', 'Frequency')

data_cond5 = cond5_key %>%
  mutate(Frequency = as.numeric(Frequency) * 5)

data_cond5 = data_cond5 %>%
  uncount(Frequency) %>%
  mutate(Frequency = 1)
```

## Condition 6: (nem type and token) 12 token 12 type (dan 3 token 3 type)

```{r}

cond6 = read_csv('../Conditions/Condition6.csv') 
cond6 = cond6 %>%
    mutate(stem = orthoCoding(stem)) %>%
  mutate(type = case_when(
    suffix == 'dan' | suffix == 'sil' ~ 'big_pl',
    suffix == 'none' ~ 'big_sg',
    suffix == 'nem' | suffix == 'shoon' ~ 'dim_sg'
  ))
  
cond6 = cond6 %>%
  mutate(key = paste0(stem, '_', type))

cond6_key = cond6 %>%
  group_by(key, suffix) %>%
  summarize(frequency = table(key))

colnames(cond6_key) = c('Cues', 'Outcomes', 'Frequency')

data_cond6 = cond6_key %>%
  mutate(Frequency = as.numeric(Frequency) * 5)

data_cond6 = data_cond6 %>%
  uncount(Frequency) %>%
  mutate(Frequency = 1)
```

```{r}

data_cond1_configural = data_cond1 %>%
  mutate(Cues = case_when(
    str_ends(Cues, "big_pl") ~ paste0(Cues, "_big.pl"),
    str_ends(Cues, "big_sg") ~ paste0(Cues, "_big.sg"),
    str_ends(Cues, "dim_sg") ~ paste0(Cues, "_dim.sg"),
    TRUE ~ Cues  # leave unchanged if none of these endings
  ))

data_cond2_configural = data_cond2 %>%
  mutate(Cues = case_when(
    str_ends(Cues, "big_pl") ~ paste0(Cues, "_big.pl"),
    str_ends(Cues, "big_sg") ~ paste0(Cues, "_big.sg"),
    str_ends(Cues, "dim_sg") ~ paste0(Cues, "_dim.sg"),
    TRUE ~ Cues  # leave unchanged if none of these endings
  ))

data_cond3_configural = data_cond3 %>%
  mutate(Cues = case_when(
    str_ends(Cues, "big_pl") ~ paste0(Cues, "_big.pl"),
    str_ends(Cues, "big_sg") ~ paste0(Cues, "_big.sg"),
    str_ends(Cues, "dim_sg") ~ paste0(Cues, "_dim.sg"),
    TRUE ~ Cues  # leave unchanged if none of these endings
  ))

data_cond4_configural = data_cond4 %>%
  mutate(Cues = case_when(
    str_ends(Cues, "big_pl") ~ paste0(Cues, "_big.pl"),
    str_ends(Cues, "big_sg") ~ paste0(Cues, "_big.sg"),
    str_ends(Cues, "dim_sg") ~ paste0(Cues, "_dim.sg"),
    TRUE ~ Cues  # leave unchanged if none of these endings
  ))

data_cond5_configural = data_cond5 %>%
  mutate(Cues = case_when(
    str_ends(Cues, "big_pl") ~ paste0(Cues, "_big.pl"),
    str_ends(Cues, "big_sg") ~ paste0(Cues, "_big.sg"),
    str_ends(Cues, "dim_sg") ~ paste0(Cues, "_dim.sg"),
    TRUE ~ Cues  # leave unchanged if none of these endings
  ))

data_cond6_configural = data_cond6 %>%
  mutate(Cues = case_when(
    str_ends(Cues, "big_pl") ~ paste0(Cues, "_big.pl"),
    str_ends(Cues, "big_sg") ~ paste0(Cues, "_big.sg"),
    str_ends(Cues, "dim_sg") ~ paste0(Cues, "_dim.sg"),
    TRUE ~ Cues  # leave unchanged if none of these endings
  ))
```

# single function for production

```{r}
human_data = read_csv('../Data/fixed_effects_df_all.csv') %>%
  filter(Task == 'prod')
```

```{r}
semantic_cues = c('dim', 'pl', 'big', 'sg', 'big.pl', 'big.sg', 'dim.sg', 'dim.pl')
run_rw_production = function(
  n_sims = 5,
  Alpha,
  SemAlpha,
  Beta,
  configural_list,
  prod_file = '../Conditions/production_condition.csv',
  hum   = human_data
)
 {

  library(tidyverse)
  library(purrr)
  message("Running production: Alpha=", Alpha,
          " SemAlpha=", SemAlpha,
          " Beta=", Beta)
  # -----------------------------
  # 1. helper that runs RW once
  # -----------------------------
  run_rw = function(config_data) {
    map_dfr(1:n_sims, function(i){
      Rescorla_modified_alpha_for_semantic_cues(
        cuesOutcomes = config_data[sample(nrow(config_data)),],
        logistic = TRUE,
        Alpha = Alpha,
        SemAlpha = SemAlpha,
        Beta = Beta
      ) %>%
        as.data.frame() %>%
        tibble::rownames_to_column("cue") %>%
        mutate(sim = i)
    })
  }

  # run RW for each condition
  rw_results = map(configural_list, run_rw)

  # -----------------------------
  # 2. Load & preprocess prod file
  # -----------------------------
  data_prod = read_csv(prod_file, show_col_types = FALSE) %>%
    mutate(
      stem = orthoCoding(prod_label),
      type = case_when(
        str_detect(file, "dim_sg") ~ "dim_sg_dim.sg",
        str_detect(file, "_2")     ~ "big_pl_big.pl",
        str_detect(file, "dim_pl") ~ "dim_pl",
        TRUE                       ~ NA_character_
      ),
      row_id = row_number()
    )

  data_prod = map_dfr(1:n_sims, ~ mutate(data_prod, sim = .x))

  # ----------------------------------------------------------
  # 3. helper that joins & computes activations for one cond
  # ----------------------------------------------------------
  process_one_condition = function(prod_data, rw_data, cond_num){

    prod_cond = prod_data %>%
      mutate(key = paste0(stem, "_", type)) %>%
      group_by(sim) %>%
      mutate(row_id = row_number())

    res = prod_cond %>%
      separate_rows(key, sep = "_") %>%
      left_join(rw_data, by = c("key" = "cue", "sim")) %>%
      group_by(row_id, sim) %>%
      summarize(
        dan_activations   = sum(dan,   na.rm = TRUE),
        sil_activations   = sum(sil,   na.rm = TRUE),
        nem_activations   = sum(nem,   na.rm = TRUE),
        shoon_activations = sum(shoon, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      left_join(prod_data, by = c("row_id", "sim")) %>%
      mutate(
        condition = cond_num,
        freq_minus_infreq =
          if (cond_num %in% c(1, 2, 3))
            dan_activations - nem_activations
          else
            nem_activations - dan_activations
      )

    res
  }

  # process all conditions
  cond_ids = seq_along(rw_results)

  prod_results = map2_dfr(
    cond_ids,
    rw_results,
    ~ process_one_condition(data_prod, .y, .x)
  )

  # ----------------------------------------------------------
  # 4. compute dv for each condition (vectorised, grouped)
  # ----------------------------------------------------------
  prod_results = prod_results %>%
    group_by(prod_label, sim, condition) %>%
    mutate(
      dv = case_when(
        type == "dim_pl" ~ freq_minus_infreq,
        condition %in% c(1, 2, 3) ~
          dan_activations[type == "big_pl_big.pl"][1] -
          nem_activations[type == "dim_sg_dim.sg"][1],
        condition %in% c(4, 5, 6) ~
          nem_activations[type == "dim_sg_dim.sg"][1] -
          dan_activations[type == "big_pl_big.pl"][1]
      )
    )

  # ----------------------------------------------------------
  # 5. final summarization
  # ----------------------------------------------------------
  out = prod_results %>%
    mutate(
      meaning = case_when(
        type %in% c("dim_sg_dim.sg", "big_pl_big.pl") ~ "original",
        type == "dim_pl"                              ~ "novel",
        TRUE                                          ~ NA_character_
      ),
      # collapse 1/4 → 1, 2/5 → 2, 3/6 → 3
      condition = case_when(
        condition %in% c(1, 4) ~ 1,
        condition %in% c(2, 5) ~ 2,
        condition %in% c(3, 6) ~ 3
      )
    ) %>%
    group_by(meaning, prod_condition, condition, sim) %>%
    summarize(
      mean_freq_diff = mean(freq_minus_infreq),
      .groups = "keep"
    ) %>%
    group_by(meaning, prod_condition, condition) %>%
    summarize(
      mean_freq_diff_v2 = mean(mean_freq_diff),
      ci2.5  = quantile(mean_freq_diff, 0.025, na.rm = TRUE),
      ci97.5 = quantile(mean_freq_diff, 0.975, na.rm = TRUE),
      .groups = "keep"
    )
  
  hum2 = hum %>%
  mutate(
    Meaning   = tolower(Meaning),
    Condition = case_when(Condition == 'cond1' ~ 1,
                          Condition == 'cond2' ~ 2,
                          Condition == 'cond3' ~ 3),
    Stem      = tolower(Stem)
  ) %>%
  dplyr::select(Meaning, Condition, Stem, Estimate)

  out = out %>%
    left_join(
      hum2,
      by = join_by(
        meaning == Meaning,
        condition == Condition,
        prod_condition == Stem
      )
    ) %>%
    mutate(
      mse = (mean_freq_diff_v2 - Estimate)^2
    )


  return(out)
}


results = run_rw_production(
  n_sims = 100,
  Alpha = 0.05,
  SemAlpha = 0.25,
  Beta = 0.1,
  configural_list = list(
    data_cond1_configural,
    data_cond2_configural,
    data_cond3_configural,
    data_cond4_configural,
    data_cond5_configural,
    data_cond6_configural),
    hum = human_data
)


```

## Plot

```{r}
library(dplyr)
library(tidyr)

semalpha_vals = seq(0, 1, by = 0.05)
beta_vals     = seq(0, 1, by = 0.05)
alpha_vals    = seq(0, 1, by = 0.05)

param_grid = tidyr::crossing(
  SemAlpha = semalpha_vals,
  Beta     = beta_vals,
  Alpha    = alpha_vals
)

results_all <- param_grid %>%
  mutate(
    model_results = pmap(
      list(SemAlpha, Beta, Alpha),
      ~ run_rw_production(
          n_sims = 50,
          Alpha    = ..3,
          SemAlpha = ..1,
          Beta     = ..2,
          configural_list = list(
            data_cond1_configural,
            data_cond2_configural,
            data_cond3_configural,
            data_cond4_configural,
            data_cond5_configural,
            data_cond6_configural
          ),
          hum = human_data
      )
    )
  ) %>%
  unnest(model_results)

results_all = results_all %>%
  group_by(SemAlpha, Beta, Alpha) %>%
  mutate(mean_mse = mean(mse, na.rm = TRUE))

```

```{r}
results_all_prod = read_csv('../Data/grid_search_results_all.csv')
pattern_scores <- results_all_prod %>%
  group_by(Alpha, Beta, SemAlpha) %>%
  summarize(
    spearman = cor(
      Estimate,
      mean_freq_diff_v2,
      method = "spearman"
    ),
    kendall = cor(
      Estimate,
      mean_freq_diff_v2,
      method = "kendall"
    ),
    .groups = "drop"
  ) %>%
  arrange(desc(spearman))

# pattern_scores <- results_all_prod %>%
#   ungroup() %>%
#   filter(condition == 2) %>%
#   group_by(Alpha, Beta, SemAlpha) %>%
#   summarize(
#     spearman = cor(
#       Estimate,
#       mean_freq_diff_v2,
#       method = "spearman"
#     ),
#     kendall = cor(
#       Estimate,
#       mean_freq_diff_v2,
#       method = "kendall"
#     ),
#     .groups = "drop"
#   ) %>%
#   arrange(desc(spearman))



results_plot = results_all_prod %>%
  filter(
    near(Alpha, pattern_scores$Alpha[1]),
    near(Beta, pattern_scores$Beta[1]),
    near(SemAlpha, pattern_scores$SemAlpha[1])
  )

#write_csv(results_plot, '../Data/grid_search_results_best_params.csv')


p1 = ggplot(data = results_plot, aes(x = meaning, y = invlogit(mean_freq_diff_v2), fill = prod_condition)) +
  geom_col(position = "dodge") +
  ylim(c(0,1)) +
  ggtitle('configural cues + mod alpha') +
  facet_wrap(~condition)

p2 = ggplot(data = results_lowest_mse, aes(x = meaning, y = invlogit(Estimate), fill = prod_condition)) +
  geom_col(position = "dodge") +
  ylim(c(0,1)) +
  ggtitle('configural cues + mod alpha') +
  facet_wrap(~condition)

ggarrange(p1, p2)

```

## Configural Cue Saliency Grid Search

Grid search over `ConfAlpha` (saliency of configural cues e.g. `dim.pl`, `big.pl`) with `Alpha`, `Beta`, and `SemAlpha` fixed to the best-fitting production parameters from the paper (0.05, 0.6, 0.65 respectively).

```{r}
run_rw_production_conf = function(
  n_sims = 5,
  Alpha,
  SemAlpha,
  ConfAlpha,
  Beta,
  configural_list,
  prod_file = '../Conditions/production_condition.csv',
  hum = human_data
) {
  library(tidyverse)
  library(purrr)
  message("Running production: Alpha=", Alpha,
          " SemAlpha=", SemAlpha,
          " ConfAlpha=", ConfAlpha,
          " Beta=", Beta)

  run_rw = function(config_data) {
    map_dfr(1:n_sims, function(i) {
      Rescorla_modified_alpha_for_configural_cues(
        cuesOutcomes = config_data[sample(nrow(config_data)), ],
        logistic  = TRUE,
        Alpha     = Alpha,
        SemAlpha  = SemAlpha,
        ConfAlpha = ConfAlpha,
        Beta      = Beta
      ) %>%
        as.data.frame() %>%
        tibble::rownames_to_column("cue") %>%
        mutate(sim = i)
    })
  }

  rw_results = map(configural_list, run_rw)

  data_prod = read_csv(prod_file, show_col_types = FALSE) %>%
    mutate(
      stem = orthoCoding(prod_label),
      type = case_when(
        str_detect(file, "dim_sg") ~ "dim_sg_dim.sg",
        str_detect(file, "_2")     ~ "big_pl_big.pl",
        str_detect(file, "dim_pl") ~ "dim_pl",
        TRUE                       ~ NA_character_
      ),
      row_id = row_number()
    )

  data_prod = map_dfr(1:n_sims, ~ mutate(data_prod, sim = .x))

  process_one_condition = function(prod_data, rw_data, cond_num) {
    prod_cond = prod_data %>%
      mutate(key = paste0(stem, "_", type)) %>%
      group_by(sim) %>%
      mutate(row_id = row_number())

    res = prod_cond %>%
      separate_rows(key, sep = "_") %>%
      left_join(rw_data, by = c("key" = "cue", "sim")) %>%
      group_by(row_id, sim) %>%
      summarize(
        dan_activations   = sum(dan,   na.rm = TRUE),
        sil_activations   = sum(sil,   na.rm = TRUE),
        nem_activations   = sum(nem,   na.rm = TRUE),
        shoon_activations = sum(shoon, na.rm = TRUE),
        .groups = "drop"
      ) %>%
      left_join(prod_data, by = c("row_id", "sim")) %>%
      mutate(
        condition = cond_num,
        freq_minus_infreq =
          if (cond_num %in% c(1, 2, 3))
            dan_activations - nem_activations
          else
            nem_activations - dan_activations
      )
    res
  }

  cond_ids = seq_along(rw_results)

  prod_results = map2_dfr(
    cond_ids,
    rw_results,
    ~ process_one_condition(data_prod, .y, .x)
  )

  prod_results = prod_results %>%
    group_by(prod_label, sim, condition) %>%
    mutate(
      dv = case_when(
        type == "dim_pl" ~ freq_minus_infreq,
        condition %in% c(1, 2, 3) ~
          dan_activations[type == "big_pl_big.pl"][1] -
          nem_activations[type == "dim_sg_dim.sg"][1],
        condition %in% c(4, 5, 6) ~
          nem_activations[type == "dim_sg_dim.sg"][1] -
          dan_activations[type == "big_pl_big.pl"][1]
      )
    )

  out = prod_results %>%
    mutate(
      meaning = case_when(
        type %in% c("dim_sg_dim.sg", "big_pl_big.pl") ~ "original",
        type == "dim_pl"                               ~ "novel",
        TRUE                                           ~ NA_character_
      ),
      condition = case_when(
        condition %in% c(1, 4) ~ 1,
        condition %in% c(2, 5) ~ 2,
        condition %in% c(3, 6) ~ 3
      )
    ) %>%
    group_by(meaning, prod_condition, condition, sim) %>%
    summarize(
      mean_freq_diff = mean(freq_minus_infreq),
      .groups = "keep"
    ) %>%
    group_by(meaning, prod_condition, condition) %>%
    summarize(
      mean_freq_diff_v2 = mean(mean_freq_diff),
      ci2.5  = quantile(mean_freq_diff, 0.025, na.rm = TRUE),
      ci97.5 = quantile(mean_freq_diff, 0.975, na.rm = TRUE),
      .groups = "keep"
    )

  hum2 = hum %>%
    mutate(
      Meaning   = tolower(Meaning),
      Condition = case_when(Condition == 'cond1' ~ 1,
                            Condition == 'cond2' ~ 2,
                            Condition == 'cond3' ~ 3),
      Stem      = tolower(Stem)
    ) %>%
    dplyr::select(Meaning, Condition, Stem, Estimate)

  out = out %>%
    left_join(
      hum2,
      by = join_by(
        meaning    == Meaning,
        condition  == Condition,
        prod_condition == Stem
      )
    ) %>%
    mutate(mse = (mean_freq_diff_v2 - Estimate)^2)

  return(out)
}
```

```{r}
plan(multisession, workers = 4)
handlers(global = TRUE)
handlers("txtprogressbar")

param_grid_conf = tidyr::crossing(
  ConfAlpha = seq(0, 1, by = 0.05),
  SemAlpha  = seq(0, 1, by = 0.05),
  Beta      = seq(0, 1, by = 0.05),
  Alpha     = seq(0, 1, by = 0.05)
)

results_all_conf = param_grid_conf %>%
  mutate(
    model_results = future_pmap(
      list(ConfAlpha, SemAlpha, Beta, Alpha),
      ~ run_rw_production_conf(
          n_sims    = 50,
          Alpha     = ..4,
          SemAlpha  = ..2,
          ConfAlpha = ..1,
          Beta      = ..3,
          configural_list = list(
            data_cond1_configural,
            data_cond2_configural,
            data_cond3_configural,
            data_cond4_configural,
            data_cond5_configural,
            data_cond6_configural
          ),
          hum = human_data
      ),
      .options = furrr_options(packages = c("tidyverse", "ndl", "arm"),
                               seed = 964),
      .progress = TRUE
    )
  ) %>%
  unnest(model_results)

plan(sequential)

results_all_conf = results_all_conf %>%
  group_by(ConfAlpha, SemAlpha, Beta, Alpha) %>%
  mutate(mean_mse = mean(mse, na.rm = TRUE))
```

```{r}
pattern_scores_conf = results_all_conf %>%
  group_by(Alpha, Beta, SemAlpha, ConfAlpha) %>%
  summarize(
    spearman = cor(Estimate, mean_freq_diff_v2, method = "spearman"),
    kendall  = cor(Estimate, mean_freq_diff_v2, method = "kendall"),
    mean_mse = mean(mse, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(spearman), desc(kendall))

write_csv(results_all_conf, '../Data/grid_search_results_conf_alpha.csv')
```

```{r}
top_spearman = pattern_scores_conf %>%
  filter(spearman == max(spearman))

top_both = pattern_scores_conf %>%
  filter(spearman == max(spearman), kendall == max(kendall[spearman == max(spearman)]))

cat('Parameter sets tied at best Spearman (', round(max(pattern_scores_conf$spearman), 4), '):', nrow(top_spearman), '\n')
cat('Of those, tied at best Kendall (', round(top_both$kendall[1], 4), '):', nrow(top_both), '\n\n')

cat('--- Distribution of parameters among top Spearman sets ---\n')
top_spearman %>%
  summarize(across(c(Alpha, Beta, SemAlpha, ConfAlpha),
                   list(min = min, max = max, n_unique = n_distinct))) %>%
  print()
```

```{r}
best_conf_alpha = pattern_scores_conf$ConfAlpha[1]
best_conf_semalpha = pattern_scores_conf$SemAlpha[1]
best_conf_beta = pattern_scores_conf$Beta[1]
best_conf_alpha_stem = pattern_scores_conf$Alpha[1]

conf_model_data = results_all_conf %>%
  filter(
    near(ConfAlpha, best_conf_alpha),
    near(SemAlpha,  best_conf_semalpha),
    near(Beta,      best_conf_beta),
    near(Alpha,     best_conf_alpha_stem)
  ) %>%
  mutate(
    model_type = 'RW Sims',
    Prob  = arm::invlogit(mean_freq_diff_v2),
    Lower = arm::invlogit(ci2.5),
    Upper = arm::invlogit(ci97.5)
  ) %>%
  dplyr::select(meaning, prod_condition, condition, Prob, model_type, Lower, Upper)

conf_human_data = read_csv('../Data/fixed_effects_df_all.csv') %>%
  filter(Task == 'prod') %>%
  mutate(model_type = 'Human') %>%
  rename(meaning = Meaning, condition = Condition, prod_condition = Stem) %>%
  mutate(condition = case_when(
    condition == 'cond1' ~ 1,
    condition == 'cond2' ~ 2,
    condition == 'cond3' ~ 3
  )) %>%
  dplyr::select(meaning, prod_condition, condition, Prob, model_type, Lower, Upper)

conf_all_data = full_join(conf_model_data, conf_human_data) %>%
  mutate(across(where(is.character), str_to_title)) %>%
  mutate(Condition = case_when(
    condition == 1 ~ 'Type Frequency',
    condition == 2 ~ 'Token Frequency',
    condition == 3 ~ 'Type-Token Frequency'
  ))

conf_all_data$Condition = factor(
  conf_all_data$Condition,
  levels = c('Type Frequency', 'Token Frequency', 'Type-Token Frequency')
)

ggplot(conf_all_data, aes(x = model_type, y = Prob, fill = prod_condition)) +
  geom_col(position = position_dodge(width = 0.9)) +
  geom_errorbar(
    aes(ymin = Lower, ymax = Upper),
    width = 0.2,
    position = position_dodge(width = 0.9)
  ) +
  xlab('Human Data vs Model Predictions') +
  ylab('Probability of the Frequent Meaning') +
  ylim(c(0, 1)) +
  facet_grid(meaning ~ Condition) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle(paste0('Configural Cue Model (Alpha=', best_conf_alpha_stem,
                 ', Beta=', best_conf_beta,
                 ', SemAlpha=', best_conf_semalpha,
                 ', ConfAlpha=', best_conf_alpha, ')'))
```
