---
title: "Generalizability Results Summary"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(brms)
library(knitr)
library(kableExtra)

DATA_DIR <- normalizePath('../Data')
load_m   <- function(name) readRDS(file.path(DATA_DIR, paste0(name, '.rds')))
```

```{r helpers}
# Extract fixef table with 95% CIs and % posterior samples > 0
fixef_table <- function(model, row_labels = NULL) {
  draws <- as.data.frame(fixef(model, summary = FALSE))
  pgt0  <- draws %>%
    pivot_longer(everything(), names_to = 'term', values_to = 'est') %>%
    group_by(term) %>%
    summarize(pgt0 = mean(est > 0) * 100, .groups = 'drop')

  out <- as.data.frame(fixef(model)) %>%
    rownames_to_column('term') %>%
    left_join(pgt0, by = 'term') %>%
    mutate(
      `95% CI` = paste0('[', round(Q2.5, 3), ', ', round(Q97.5, 3), ']'),
      `% > 0`  = paste0(round(pgt0, 1), '%'),
      Estimate = round(Estimate, 3),
      Est.Error = round(Est.Error, 3)
    ) %>%
    select(term, Estimate, Est.Error, `95% CI`, `% > 0`)

  if (!is.null(row_labels)) out$term <- row_labels
  out %>% rename(Term = term, SE = Est.Error)
}

fmt_table <- function(df, caption = '') {
  kable(df, caption = caption, align = c('l', 'r', 'r', 'c', 'r')) %>%
    kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),
                  full_width = FALSE) %>%
    row_spec(0, bold = TRUE)
}

# Run hypothesis() contrasts and return a formatted kable
hyp_table <- function(model, hyps, labels = NULL, caption = '') {
  res <- hypothesis(model, hyps)$hypothesis %>%
    mutate(
      `95% CI` = paste0('[', round(CI.Lower, 3), ', ', round(CI.Upper, 3), ']'),
      Estimate  = round(Estimate, 3),
      `% Post` = paste0(round(Post.Prob * 100, 1), '%')
    ) %>%
    select(Hypothesis, Estimate, `95% CI`, `% Post`)
  if (!is.null(labels)) res$Hypothesis <- labels
  kable(res, caption = caption, align = c('l', 'r', 'c', 'r')) %>%
    kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),
                  full_width = FALSE) %>%
    row_spec(0, bold = TRUE)
}

# Standard contrast strings for a sum-coded 3-level condition
# (condition1 = Type, condition2 = Token, reference = Type-Token)
cond_contrasts <- function(suffix = '') {
  s <- if (nchar(suffix)) paste0(':', suffix) else ''
  c(
    paste0('condition1', s, ' - condition2', s, ' = 0'),
    paste0('2*condition1', s, ' + condition2', s, ' = 0'),
    paste0('condition1', s, ' + 2*condition2', s, ' = 0')
  )
}
cond_labels <- c('Type vs Token', 'Type vs Type-Token', 'Token vs Type-Token')

add_loo_safe <- function(model) {
  tryCatch(add_criterion(model, 'loo'), error = function(e) model)
}
```

---

# Coding Notes

**Condition** (sum-coded, reference = Type-Token Frequency):

- `condition1` = Type Frequency vs. grand mean
- `condition2` = Token Frequency vs. grand mean
- Type-Token is the implicit reference (coded −1 on both contrasts)

**Meaning** (sum-coded): `meaning1` = Novel Meaning vs. grand mean
**Stem** (sum-coded): `stem_condition1` = Novel Stem vs. grand mean
**95% CI** = 2.5th–97.5th percentile of posterior samples
**% > 0** = proportion of posterior samples where coefficient > 0 (analogous to 1 − *p*/2 for positive effects)

---

# 1. Production Task

How does type, token, and type-token frequency affect suffix production, overall and broken down by meaning (original vs. novel) and stem familiarity?

## 1.1 Condition × Meaning

*Model:* `frequency ~ condition * meaning + (1 + meaning | participant)`

```{r prod-both}
m_prod_both <- load_m('model_prod_both')

labels_2way <- c('Intercept',
                 'Type Frequency', 'Token Frequency',
                 'Novel Meaning',
                 'Type Freq × Novel Meaning', 'Token Freq × Novel Meaning')

fixef_table(m_prod_both, labels_2way) %>%
  fmt_table('Production: Condition × Meaning')
```

**Interpretation guide:**

- `Type Frequency` / `Token Frequency`: how each condition differs from the grand mean in suffix production (positive = more frequent-suffix responses)
- `Novel Meaning`: whether novel-meaning items differ from original-meaning items on average
- Interactions: whether the condition effect is bigger or smaller for novel-meaning items

## 1.2 Condition × Meaning × Stem Type

*Model:* `frequency ~ condition * meaning * stem_condition + (1 + meaning | participant)`

```{r prod-both-stem}
m_prod_both_stem <- load_m('model_prod_both_stem')

labels_3way <- c('Intercept',
                 'Type Frequency', 'Token Frequency',
                 'Novel Meaning', 'Novel Stem',
                 'Type Freq × Novel Meaning', 'Token Freq × Novel Meaning',
                 'Type Freq × Novel Stem',   'Token Freq × Novel Stem',
                 'Novel Meaning × Novel Stem',
                 'Type Freq × Novel Meaning × Novel Stem',
                 'Token Freq × Novel Meaning × Novel Stem')

fixef_table(m_prod_both_stem, labels_3way) %>%
  fmt_table('Production: Condition × Meaning × Stem Type')
```

## 1.3 Pairwise Contrasts (Production)

*% Post = posterior probability that the contrast is in the stated direction.*

### Condition (marginal)
```{r prod-hyp-cond}
hyp_table(m_prod_both_stem, cond_contrasts(), cond_labels,
          'Production: Pairwise Condition Contrasts (marginal)')
```

### Meaning and Stem (marginal)
```{r prod-hyp-ms}
hyp_table(m_prod_both_stem,
          c('2*meaning1 = 0', '2*stem_condition1 = 0'),
          c('Novel vs Original Meaning', 'Novel vs Familiar Stem'),
          'Production: Meaning and Stem Contrasts (marginal)')
```

### Condition contrasts within Novel Meaning
```{r prod-hyp-cond-novel-meaning}
hyp_table(m_prod_both_stem,
          cond_contrasts('meaning1'),
          paste0(cond_labels, ' | Novel Meaning'),
          'Production: Condition Contrasts within Novel Meaning')
```

### Condition contrasts within Novel Stem
```{r prod-hyp-cond-novel-stem}
hyp_table(m_prod_both_stem,
          cond_contrasts('stem_condition1'),
          paste0(cond_labels, ' | Novel Stem'),
          'Production: Condition Contrasts within Novel Stem')
```

### Meaning contrast within each Condition
```{r prod-hyp-meaning-by-cond}
hyp_table(m_prod_both_stem,
          c('2*meaning1 + 2*condition1:meaning1 = 0',
            '2*meaning1 + 2*condition2:meaning1 = 0',
            '2*meaning1 - 2*condition1:meaning1 - 2*condition2:meaning1 = 0'),
          c('Novel vs Original | Type Freq',
            'Novel vs Original | Token Freq',
            'Novel vs Original | Type-Token Freq'),
          'Production: Meaning Contrast within each Condition')
```

### Stem contrast within each Condition
```{r prod-hyp-stem-by-cond}
hyp_table(m_prod_both_stem,
          c('2*stem_condition1 + 2*condition1:stem_condition1 = 0',
            '2*stem_condition1 + 2*condition2:stem_condition1 = 0',
            '2*stem_condition1 - 2*condition1:stem_condition1 - 2*condition2:stem_condition1 = 0'),
          c('Novel vs Familiar Stem | Type Freq',
            'Novel vs Familiar Stem | Token Freq',
            'Novel vs Familiar Stem | Type-Token Freq'),
          'Production: Stem Contrast within each Condition')
```

---

# 2. Form-Choice (2AFC) Task

## 2.1 Condition × Meaning

*Model:* `frequency ~ condition * meaning + (1 + meaning | participant)`

```{r afc-both}
m_2afc_both <- load_m('model_2afc_both')

fixef_table(m_2afc_both, labels_2way) %>%
  fmt_table('2AFC: Condition × Meaning')
```

## 2.2 Condition × Meaning × Stem Type

*Model:* `frequency ~ condition * meaning * stem_condition + (1 + meaning | participant)`

```{r afc-both-stem}
m_2afc_both_stem <- load_m('model_2afc_both_stem')

fixef_table(m_2afc_both_stem, labels_3way) %>%
  fmt_table('2AFC: Condition × Meaning × Stem Type')
```

## 2.3 Pairwise Contrasts (2AFC)

### Condition (marginal)
```{r afc-hyp-cond}
hyp_table(m_2afc_both_stem, cond_contrasts(), cond_labels,
          '2AFC: Pairwise Condition Contrasts (marginal)')
```

### Meaning and Stem (marginal)
```{r afc-hyp-ms}
hyp_table(m_2afc_both_stem,
          c('2*meaning1 = 0', '2*stem_condition1 = 0'),
          c('Novel vs Original Meaning', 'Novel vs Familiar Stem'),
          '2AFC: Meaning and Stem Contrasts (marginal)')
```

### Condition contrasts within Novel Meaning
```{r afc-hyp-cond-novel-meaning}
hyp_table(m_2afc_both_stem,
          cond_contrasts('meaning1'),
          paste0(cond_labels, ' | Novel Meaning'),
          '2AFC: Condition Contrasts within Novel Meaning')
```

### Condition contrasts within Novel Stem
```{r afc-hyp-cond-novel-stem}
hyp_table(m_2afc_both_stem,
          cond_contrasts('stem_condition1'),
          paste0(cond_labels, ' | Novel Stem'),
          '2AFC: Condition Contrasts within Novel Stem')
```

### Meaning contrast within each Condition
```{r afc-hyp-meaning-by-cond}
hyp_table(m_2afc_both_stem,
          c('2*meaning1 + 2*condition1:meaning1 = 0',
            '2*meaning1 + 2*condition2:meaning1 = 0',
            '2*meaning1 - 2*condition1:meaning1 - 2*condition2:meaning1 = 0'),
          c('Novel vs Original | Type Freq',
            'Novel vs Original | Token Freq',
            'Novel vs Original | Type-Token Freq'),
          '2AFC: Meaning Contrast within each Condition')
```

### Stem contrast within each Condition
```{r afc-hyp-stem-by-cond}
hyp_table(m_2afc_both_stem,
          c('2*stem_condition1 + 2*condition1:stem_condition1 = 0',
            '2*stem_condition1 + 2*condition2:stem_condition1 = 0',
            '2*stem_condition1 - 2*condition1:stem_condition1 - 2*condition2:stem_condition1 = 0'),
          c('Novel vs Familiar Stem | Type Freq',
            'Novel vs Familiar Stem | Token Freq',
            'Novel vs Familiar Stem | Type-Token Freq'),
          '2AFC: Stem Contrast within each Condition')
```

---

# 3. Production + 2AFC Combined

*Model:* `frequency ~ condition * meaning * stem_condition * task + (1 + meaning * task | participant)`

Tests whether condition effects differ across tasks (production vs. form choice).

```{r combined}
m_both_tasks <- load_m('model_2afc_prod_both_stem')

fixef_table(m_both_tasks) %>%
  fmt_table('Production + 2AFC: Full Model')
```

---

# 4. Comprehension Task

Comprehension uses a different design: `condition_numeric` compares token-frequency (12-12) and type-frequency (3-3) training regimens against the type-token baseline.

## 4.1 Condition Effect

*Model:* `meaning ~ condition_numeric + (1 | participant)`

```{r comp-main}
m_comp_humans <- load_m('model_comprehension_numeric_humans')

comp_labels <- c('Intercept', 'Token Freq (12-12)', 'Type Freq (3-3)')
fixef_table(m_comp_humans, comp_labels) %>%
  fmt_table('Comprehension: Condition Effect')
```

## 4.2 Condition × Stem Type

*Model:* `meaning ~ condition_numeric * stem_condition + (1 | participant)`

```{r comp-stem}
m_comp_stem <- load_m('model_comprehension_numeric_stem_humans')

comp_stem_labels <- c('Intercept',
                      'Token Freq (12-12)', 'Type Freq (3-3)',
                      'Novel Stem',
                      'Token Freq × Novel Stem', 'Type Freq × Novel Stem')
fixef_table(m_comp_stem, comp_stem_labels) %>%
  fmt_table('Comprehension: Condition × Stem Type')
```

## 4.3 Pairwise Contrasts (Comprehension)

*Note: comprehension uses treatment coding; the baseline is Type-Token (12-12 and 3-3 are deviations from it).*

```{r comp-hyp}
hyp_table(m_comp_stem,
          c('condition_numeric3M3 - condition_numeric12M12 = 0',
            '2*stem_condition1 = 0',
            '2*stem_condition1 + 2*condition_numeric12M12:stem_condition1 = 0',
            '2*stem_condition1 + 2*condition_numeric3M3:stem_condition1 = 0',
            '2*stem_condition1 - 2*condition_numeric12M12:stem_condition1 - 2*condition_numeric3M3:stem_condition1 = 0'),
          c('Type Freq (3-3) vs Token Freq (12-12)',
            'Novel vs Familiar Stem (marginal)',
            'Novel vs Familiar Stem | Token Freq (12-12)',
            'Novel vs Familiar Stem | Type Freq (3-3)',
            'Novel vs Familiar Stem | Type-Token (baseline)'),
          'Comprehension: Key Pairwise Contrasts')
```

---

# 5. Rescorla-Wagner Simulations

## 5.1 LOO Model Comparison

Which RW model variant best predicts human production choices?

| Model | Description |
|---|---|
| `Only RW Activation` | Standard RW: stem bigrams + type label |
| `Stem and Meaning (not by Condition)` | Standard RW + condition as additive covariate |
| `Stem and Meaning by Condition` | Standard RW × condition interaction |
| `Only Configural Cues` | Configural RW: stem-meaning compound cues |
| `Only Increased Saliency` | Modified α only (no configural cues) |
| `Configural + Increased Saliency` | Configural + modified α (best grid-search params) |
| `Configural + Saliency × Condition` | Above, with condition interaction |
| `Configural + Saliency + Original Preds` | Above, plus condition × meaning × stem |
| `Original Statistical Predictors` | Human condition × meaning × stem baseline (no RW) |

```{r rw-loo}
m_rw_only      <- load_m('model_human_rw_preds')
m_rw_nc        <- load_m('model_prod_rw_stem_suffix_vary_no_interaction')
m_rw_bc        <- load_m('model_prod_rw_stem_suffix_vary_by_condition')
m_conf         <- load_m('model_human_conf')
m_mod_alpha    <- load_m('model_human_mod_sem_alpha')
m_conf_sem     <- load_m('model_human_conf_sem_preds')
m_conf_sem_cond<- load_m('model_human_conf_sem_preds_vary_by_condition')
m_conf_sem_orig<- load_m('model_human_conf_sem_preds_original_preds')
m_humans_only  <- load_m('model_prod_both_stem_simple_humans')

m_rw_only       <- add_loo_safe(m_rw_only)
m_rw_nc         <- add_loo_safe(m_rw_nc)
m_rw_bc         <- add_loo_safe(m_rw_bc)
m_conf          <- add_loo_safe(m_conf)
m_mod_alpha     <- add_loo_safe(m_mod_alpha)
m_conf_sem      <- add_loo_safe(m_conf_sem)
m_conf_sem_cond <- add_loo_safe(m_conf_sem_cond)
m_conf_sem_orig <- add_loo_safe(m_conf_sem_orig)
m_humans_only   <- add_loo_safe(m_humans_only)

loo_results <- loo_compare(
  m_rw_only, m_rw_nc, m_rw_bc,
  m_conf, m_mod_alpha,
  m_conf_sem, m_conf_sem_cond, m_conf_sem_orig,
  m_humans_only
)

label_lookup <- c(
  m_rw_only       = 'Only RW Activation',
  m_rw_nc         = 'Stem and Meaning Activations (not by Condition)',
  m_rw_bc         = 'Stem and Meaning Activations by Condition',
  m_conf          = 'Only Configural Cues',
  m_mod_alpha     = 'Only Increased Saliency of Semantic Cues',
  m_conf_sem      = 'Configural + Increased Saliency',
  m_conf_sem_cond = 'Configural + Increased Saliency × Condition',
  m_conf_sem_orig = 'Configural + Increased Saliency + Original Preds',
  m_humans_only   = 'Original Statistical Predictors'
)

loo_df <- as.data.frame(loo_results) %>%
  rownames_to_column('model_id') %>%
  mutate(Model = label_lookup[model_id]) %>%
  select(Model, elpd_diff, se_diff, looic, se_looic) %>%
  mutate(across(where(is.numeric), ~round(., 1))) %>%
  rename(`ELPD diff` = elpd_diff, `SE diff` = se_diff,
         LOOIC = looic, `SE LOOIC` = se_looic)

kable(loo_df, caption = 'LOO Comparison: RW Model Variants (sorted best to worst)') %>%
  kable_styling(bootstrap_options = c('striped', 'hover', 'condensed'),
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(1, background = '#d4edda')
```

*Note:* ELPD diff and SE diff are relative to the best model (row 1). Models within 2 SE of the best are not clearly distinguishable. Higher ELPD (less negative LOOIC) = better fit.

## 5.2 Best RW Model: Configural + Modified Alpha + Original Predictors

Fixed effects for the best-fitting model, showing the contribution of RW predictions on top of the original statistical structure.

```{r rw-best-model}
rw_best_labels <- c('Intercept',
                    'RW Activation (freq_minus_infreq)',
                    'Type Frequency', 'Token Frequency',
                    'Novel Meaning', 'Novel Stem',
                    'Type Freq × Novel Meaning', 'Token Freq × Novel Meaning',
                    'Type Freq × Novel Stem',   'Token Freq × Novel Stem',
                    'Novel Meaning × Novel Stem',
                    'Type Freq × Novel Meaning × Novel Stem',
                    'Token Freq × Novel Meaning × Novel Stem')

fixef_table(m_conf_sem_orig, rw_best_labels) %>%
  fmt_table('Best RW Model: Configural + Increased Saliency + Original Predictors')
```

## 5.3 Standard RW Model: Stem and Meaning Activations

For comparison, the standard (non-configural) RW predictions with and without condition interaction.

```{r rw-standard}
rw_bc_labels <- c('Intercept',
                  'RW Activation',
                  'Type Frequency', 'Token Frequency',
                  'RW × Type Frequency', 'RW × Token Frequency')

fixef_table(m_rw_bc, rw_bc_labels) %>%
  fmt_table('Standard RW: Stem and Meaning Activations by Condition')
```

## 5.4 RW Comprehension Models

Does RW activation predict comprehension accuracy, and does this vary by condition?

```{r rw-comp}
m_comp_rw      <- load_m('model_comprehension_numeric_rw')
m_comp_rw_cond <- load_m('model_comprehension_numeric_rw_by_cond')
m_comp_stem_rw <- load_m('model_comprehension_numeric_stem_rw')

fixef_table(m_comp_rw) %>%
  fmt_table('Comprehension: RW Activation Only')
```

```{r rw-comp-cond}
fixef_table(m_comp_rw_cond) %>%
  fmt_table('Comprehension: RW Activation × Condition')
```

```{r rw-comp-stem}
fixef_table(m_comp_stem_rw) %>%
  fmt_table('Comprehension: RW Activation × Condition × Stem')
```
